---
title: "Data processing for behavioral data"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Necessary data cleaning

- Interventions other than breathing exercise were included erroneously
- 40 second interventions allowed erroneously for a minority of cases
- reintervention was enabled for some users; excluded

# Deviations from preregistration

- Attrition wasn't defined in the prereg. We define it as no behavioral data in week 6.

# TODO

1. "Never started" participants (N=1,275): completed pre-survey but generated no behavioral data. These do not count towards dropouts, they are excluded entirely. 
2. why does RQ 2 only have unique participants: 218?
3. interventionDuration codes are 1.5, 3, 6, and NA, not 3, 6, 10 as per design. Is this a coding error or did the intervention not occur as planned?
     
```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)

```

# Step 1: Load and combine all CSVs

Column order varies across files; read everything as character to avoid
type-guessing failures on inconsistent columns.

```{r}

base_path  <- "../data/raw/behavioral data"

label_map  <- c(experimental1 = "ABC",
                experimental2 = "ACC",
                experimental3 = "BCC",
                control       = "CCC")

# Load pre-survey condition map (authoritative source for condition assignment)
pre_survey_path <- list.files("../data/raw/self-report data", 
                              pattern = "pre_survey", 
                              full.names = TRUE)

condition_map <- read_csv(pre_survey_path,
                          col_types = cols(.default = col_character()),
                          show_col_types = FALSE) %>%
  slice(-c(1, 2)) %>%
  filter(str_starts(uuid, "intervention-duration-study-spring-2025"),
         Finished == "True") %>%
  transmute(
    participant_id = str_extract(
      uuid,
      "[0-9A-Fa-f]{8}-[0-9A-Fa-f]{4}-[0-9A-Fa-f]{4}-[0-9A-Fa-f]{4}-[0-9A-Fa-f]{12}"
    ) %>% str_to_upper(),
    condition_presurvey = recode(group,
      control       = "CCC",
      experimental1 = "ABC",
      experimental2 = "ACC",
      experimental3 = "BCC"
    )
  ) %>%
  distinct(participant_id, .keep_all = TRUE)

dat_processed <- map_dfr(names(label_map), function(cond) {
  folder <- file.path(base_path, cond)
  files  <- list.files(folder, full.names = TRUE, pattern = "\\.csv$")

  map_dfr(files, function(f) {
    read_csv(f, col_types = cols(.default = col_character()), show_col_types = FALSE) %>%
      mutate(source_file = basename(f))
  }) %>%
    mutate(condition_folder = label_map[[cond]])
}) %>%
  mutate(
    participant_id = str_extract(
      source_file,
      "[0-9A-Fa-f]{8}-[0-9A-Fa-f]{4}-[0-9A-Fa-f]{4}-[0-9A-Fa-f]{4}-[0-9A-Fa-f]{12}"
    ) %>% str_to_upper()
  ) %>%
  # Join authoritative condition from pre-survey
  left_join(condition_map, by = "participant_id") %>%
  # For participants appearing in multiple folders, keep only rows matching
  # their pre-survey condition (resolves 7 duplicated CSVs)
  filter(condition_folder == condition_presurvey | is.na(condition_presurvey)) %>%
  mutate(condition = coalesce(condition_presurvey, condition_folder)) %>%
  select(-condition_folder, -condition_presurvey)

cat("Rows loaded:", nrow(dat_processed), "\n")

# Flag and remove rows where UUID extraction failed (filename didn't match pattern)
na_uuid_rows <- sum(is.na(dat_processed$participant_id))
if (na_uuid_rows > 0) {
  cat("WARNING: rows with NA participant_id (bad filename):", na_uuid_rows, "\n")
  na_uuid_files <- dat_processed %>% filter(is.na(participant_id)) %>% distinct(source_file)
  print(na_uuid_files)
  dat_processed <- dat_processed %>% filter(!is.na(participant_id))
}

# breathing exercise intervention only; exclude minority of 40 second interventions
# dat_processed |>
#   count(interventionType)

dat_processed <- dat_processed |>
  filter(interventionType == "breathingExercise" & 
           (is.na(interventionDuration) | interventionDuration %in% c(1.5, 3, 6)))

dat_processed |>
  count(condition, interventionDuration)

cat("Unique participants:", n_distinct(dat_processed$participant_id), "\n")
cat("Conditions:\n"); print(table(dat_processed$condition, useNA = "always"))

```

# Step 2: Coerce column types

```{r}
dat_processed <- dat_processed %>%
  mutate(
    timestamp            = as.numeric(timestamp),
    interventionDuration = as.numeric(interventionDuration),
    isReIntervention = case_when(
      isReIntervention %in% c("1", "True")  ~ TRUE,
      isReIntervention %in% c("0", "False") ~ FALSE,
      TRUE ~ NA
    )
  ) |>
  filter(is.na(isReIntervention) | isReIntervention==FALSE)

dat_processed |>
  count(isReIntervention)
```

# Step 3: Parse timestamp → datetime + study week

study_week: floor(day_since_start / 7) + 1  → day 0 = week 1

```{r}
dat_processed <- dat_processed %>%
  mutate(datetime = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),
         date     = as.Date(datetime)) %>%
  group_by(participant_id) %>%
  arrange(timestamp, .by_group = TRUE) %>%
  mutate(
    user_start      = min(timestamp, na.rm = TRUE),
    day_since_start = as.integer(difftime(
      datetime,
      as.POSIXct(user_start, origin = "1970-01-01", tz = "UTC"),
      units = "days"
    )),
    study_week = floor(day_since_start / 7) + 1
  ) %>%
  ungroup()
```

# Step 4: Flag and remove invalid data

- Non-2025 timestamps (Hanna found one participant with year-2001 data)
- Weeks > 6 (should disappear once non-2025 rows are removed)
- Missing condition

```{r}
dat_processed <- dat_processed %>%
  mutate(year = format(date, "%Y"))

invalid_year_ids <- dat_processed %>%
  filter(year != "2025") %>%
  distinct(participant_id) %>%
  pull()

cat("\nParticipants with non-2025 timestamps:", length(invalid_year_ids), "\n")
if (length(invalid_year_ids) > 0) print(invalid_year_ids)

missing_condition_ids <- dat_processed %>%
  filter(is.na(condition)) %>%
  distinct(participant_id) %>%
  pull()
cat("Participants with missing condition:", length(missing_condition_ids), "\n")

dat_processed <- dat_processed %>%
  filter(year == "2025",
         study_week <= 6,
         !is.na(condition))

cat("\nParticipants after cleaning:", n_distinct(dat_processed$participant_id), "\n")
cat("Rows after cleaning:", nrow(dat_processed), "\n")

```

# Step 5: Assign delay type from condition + study week

interventionDuration values in the CSVs are unreliable (per developer).
Delay type is derived entirely from condition + week.
  A = 3s (preregistered), B = 6s, C = 10s

```{r}
dat_processed <- dat_processed %>%
  mutate(delay_type = case_when(
    condition == "CCC"                         ~ "C",
    condition == "ABC" & study_week <= 2       ~ "A",
    condition == "ABC" & study_week <= 4       ~ "B",
    condition == "ABC"                         ~ "C",
    condition == "ACC" & study_week <= 2       ~ "A",
    condition == "ACC"                         ~ "C",
    condition == "BCC" & study_week <= 2       ~ "B",
    condition == "BCC"                         ~ "C",
    TRUE ~ NA_character_
  ))

cat("\nDelay type × condition:\n")
print(table(dat_processed$delay_type, dat_processed$condition, useNA = "always"))

```

# Step 6: Event classification variables

initial_attempt: all intervention-triggered attempts (excludes closedApp)
dismissed: user did not open the app after the intervention
executed: user opened the app after the intervention

NOTE: dismissedByStructuredIntervention is included as both attempt and
dismissal, following Hanna's approach. Confirm if correct.

```{r}

dat_processed <- dat_processed %>%
  mutate(
    initial_attempt = if_else(
      resolution %in% c("openedApp", "dismissedAppOpening",
                         "dismissedByStructuredIntervention"),
      1L, 0L, missing = 0L
    ),
    dismissed = if_else(
      resolution %in% c("dismissedAppOpening",
                         "dismissedByStructuredIntervention"),
      1L, 0L, missing = 0L
    ),
    executed = if_else(resolution == "openedApp", 1L, 0L, missing = 0L)
  )

cat("\nResolution value counts:\n")
print(dat_processed %>% count(resolution, sort = TRUE))

```

# Step 7: Flag missing resolution rows

```{r}
dat_processed <- dat_processed %>%
  mutate(flag_resolution_missing = is.na(resolution) | resolution == "")

cat("\nMissing resolution rows:", sum(dat_processed$flag_resolution_missing), "\n")
cat("Missing resolution by condition:\n")
print(dat_processed %>% filter(flag_resolution_missing) %>% count(condition))

```

# Step 8: Dropout status

dropout = 1 if participant has no activity in week 6

```{r}
dat_processed_dropout <- dat_processed %>%
  group_by(participant_id) %>%
  summarise(
    last_week = max(study_week, na.rm = TRUE),
    condition = first(condition),
    .groups   = "drop"
  ) %>%
  mutate(dropout = if_else(last_week < 6, 1L, 0L))

dat_processed <- dat_processed %>%
  left_join(dat_processed_dropout %>% select(participant_id, dropout), by = "participant_id")

cat("\nDropout counts per condition:\n")
print(dat_processed_dropout %>% count(condition, dropout))

```

# Step 9: Analytical subsets

```{r}
# RQ1: one row per participant
# dat_processed_behavioral_data_dropout

# RQ2.1 model: one row per participant, week 1 + week 6 dismissed/attempted
dat_processed_open_attempts <- dat_processed %>%
  filter(study_week %in% c(1, 6)) %>%
  group_by(participant_id, condition, study_week) %>%
  summarise(
    dismissed = sum(dismissed),
    attempted = sum(initial_attempt),
    .groups   = "drop"
  ) %>%
  pivot_wider(
    names_from  = study_week,
    values_from = c(dismissed, attempted),
    names_glue  = "{.value}_w{study_week}"
  ) 

# RQ2: initial events only, completers only, no missing resolution
cat("\nRQ2 — unique participants:", n_distinct(dat_processed_open_attempts$participant_id), "\n")
```

# Save

```{r}
dir.create("../data/processed", showWarnings = FALSE)

# saveRDS(dat_processed,      "../data/processed/dat_processed_behavioral_data.rds")
# saveRDS(df_rq1,         "../data/processed/df_rq1.rds")
# saveRDS(df_rq2,         "../data/processed/df_rq2.rds")
# saveRDS(df_rq2_1_model, "../data/processed/df_rq2_1_model.rds")
# saveRDS(df_rq2_2_model, "../data/processed/df_rq2_2_model.rds")

write_csv(dat_processed, "../data/processed/dat_processed_behavioral_data.csv")
write_csv(dat_processed_dropout, "../data/processed/dat_processed_behavioral_data_dropout.csv")
write_csv(dat_processed_open_attempts, "../data/processed/dat_processed_open_attempts.csv")
```

# Verification checks 

```{r}
multi_cond <- dat_processed %>%
  distinct(participant_id, condition) %>%
  count(participant_id) %>%
  filter(n > 1)

cat("\nParticipants in multiple conditions (should be 0):", nrow(multi_cond), "\n")
if (nrow(multi_cond) > 0) print(multi_cond)

cat("delay_type NAs (should be 0):", sum(is.na(dat_processed$delay_type)), "\n")
```

# Session info

```{r}
sessionInfo()
```


