---
title: "RQ1: Tolerability"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Deviations from preregistration

- Tolerability is a 0/1 variable, and is analyzed appropriately as a logistic regression rather than negative binomial as misspecified in the prereg.

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(broom)
library(emmeans)
library(flextable)
library(officer)

dir.create("../reports/")
dir.create("../reports/results_rq1_tolerability/")

```

# Load data

```{r}

df_rq1 <- read_csv("../data/processed/data_processed_behavioral_data_dropout.csv") %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

```

# Descriptive: dropout counts and rates per condition

```{r}

df_rq1_summary <- df_rq1 %>%
  group_by(condition) %>%
  summarise(
    n_total    = n(),
    n_dropout  = sum(dropout),
    n_complete = sum(dropout == 0),
    dropout_rate = round(n_dropout / n_total * 100, 1),
    .groups = "drop"
  )

df_rq1_summary

write_csv(df_rq1_summary, "../reports/results_rq1_tolerability/dropout_summary.csv")

```

# Weekly dropout: how many dropped out in each week

```{r}

df_weekly_dropout <- df_rq1 %>%
  filter(dropout == 1) %>%
  count(condition, last_week, name = "n_dropouts") |>
  pivot_wider(names_from = "condition", 
              values_from = "n_dropouts",
              names_prefix = "n_dropouts_")

df_weekly_dropout

write_csv(df_weekly_dropout, "../reports/results_rq1_tolerability/weekly_dropout_counts.csv")

```

# RQ1 model: binary logistic regression (dropout ~ condition)

Preregistration specified negative binomial but dropout is binary — logistic is the correct choice (confirmed by Hanna's thesis).

```{r}

model_rq1 <- glm(dropout ~ 1 + condition,
                 data = df_rq1,
                 family = binomial(link = "logit"))

summary(model_rq1)

# Tidy results with odds ratios and 95% CIs
results_rq1 <- tidy(model_rq1, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    OR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     p.value < .01  ~ "< .01",
                     p.value < .05  ~ "< .05",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  select(Predictor = term, OR, `95% CI` = CI, p) 

results_rq1

write_csv(results_rq1, "../reports/results_rq1_tolerability/model_rq1_results.csv")

# Model fit
chi_sq  <- model_rq1$null.deviance - model_rq1$deviance
df_diff <- model_rq1$df.null - model_rq1$df.residual
p_fit   <- pchisq(chi_sq, df = df_diff, lower.tail = FALSE)
r2_mcf  <- 1 - (logLik(model_rq1) / logLik(update(model_rq1, . ~ 1)))

cat(sprintf("\nModel fit: χ²(%d) = %.2f, p = %.3f, McFadden R² = %.3f\n",
            df_diff, chi_sq, p_fit, as.numeric(r2_mcf)))

```

# Pairwise comparisons (all pairs)

```{r}

pairwise_rq1 <- emmeans(model_rq1, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  p.value < .01  ~ "< .01",
                  p.value < .05  ~ "< .05",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq1

write_csv(pairwise_rq1, "../reports/results_rq1_tolerability/pairwise_rq1.csv")

```

# Word table

```{r}

doc <- read_docx() %>%
  body_add_par("RQ1: Logistic Regression — Dropout by Condition", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq1) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons (odds ratios)", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq1 %>%
                                 select(contrast, odds.ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit())

print(doc, target = "../reports/results_rq1_tolerability/results_rq1.docx")

```

# Session info

```{r}
sessionInfo()
```
