---
title: "RQ2: Effectiveness"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- replace analyses with MLE/multilevel models for proper ITT?
- check i understand and have implementd 2.1 and 2.2 correctly

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(MASS)
library(broom)
library(broom.mixed)
library(emmeans)
library(flextable)
library(officer)
library(AER)
library(lme4)
library(glmmTMB)
library(knitr)
library(kableExtra)

dir.create("../reports/", showWarnings = FALSE)
dir.create("../reports/results_rq2_effectiveness/")

```

# Load data

```{r}

df_rq2 <- read_csv("../data/processed/data_processed_behavioral_data_open_attempts.csv") %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

```

# RQ 2.1: Dismissed app openings in week 6

Model: NB regression, offset = log(attempted_w6). Covariates: dismissed_w1, attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_21 <- glm(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1,
  offset = log(attempted_w6),
  data   = df_rq2,
  family = poisson()
)
disp_test_21 <- dispersiontest(poisson_21)
cat("RQ2.1 dispersion test:", capture.output(print(disp_test_21)), sep = "\n")

zero_pct_21 <- mean(df_rq2$dismissed_w6 == 0, na.rm = TRUE) * 100
cat(sprintf("RQ2.1 zero proportion: %.1f%%\n", zero_pct_21))

```

## Main model

```{r}

model_rq2_1 <- glm.nb(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1 + offset(log(attempted_w6)),
  data = df_rq2
)

summary(model_rq2_1)

results_rq2_1 <- tidy(model_rq2_1, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p) 

results_rq2_1 |> kable() |> kable_classic()

write_csv(results_rq2_1, "../reports/results_rq2_effectiveness/model_rq2_1_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_1 <- emmeans(model_rq2_1, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq2_1 |> kable() |> kable_classic()

write_csv(pairwise_rq2_1, "../reports/results_rq2_effectiveness/pairwise_rq2_1.csv")

```

## Relative reduction: % dismissed of attempted per condition × week

```{r}

# TODO

```

# RQ 2.2: Initial app opening attempts in week 6

Model: NB regression, covariate = attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_22 <- glm(
  attempted_w6 ~ condition + attempted_w1,
  data   = df_rq2,
  family = poisson()
)
disp_test_22 <- dispersiontest(poisson_22)
cat("\nRQ2.2 dispersion test:", capture.output(print(disp_test_22)), sep = "\n")

zero_pct_22 <- mean(df_rq2$attempted_w6 == 0, na.rm = TRUE) * 100
cat(sprintf("RQ2.2 zero proportion: %.1f%%\n", zero_pct_22))

```

## Main model

```{r}

model_rq2_2 <- glm.nb(
  attempted_w6 ~ condition + attempted_w1,
  data = df_rq2
)

summary(model_rq2_2)

results_rq2_2 <- tidy(model_rq2_2, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p) 

results_rq2_2 |> kable() |> kable_classic()

write_csv(results_rq2_2, "../reports/results_rq2_effectiveness/model_rq2_2_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_2 <- emmeans(model_rq2_2, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq2_2 |> kable() |> kable_classic()

write_csv(pairwise_rq2_2, "../reports/results_rq2_effectiveness/pairwise_rq2_2.csv")

```

## Mean initial attempts per user per condition × week

```{r}

# TODO
#
# df_weekly_attempts <- df_rq2_event %>%
#   group_by(participant_id, condition, study_week) %>%
#   summarise(initial = sum(initial_attempt), .groups = "drop") %>%
#   group_by(condition, study_week) %>%
#   summarise(
#     n_users      = n(),
#     mean_initial = round(mean(initial), 2),
#     .groups = "drop"
#   )
# 
# df_weekly_attempts
# 
# write_csv(df_weekly_attempts, "../reports/results_rq2_effectiveness/weekly_attempts_by_condition.csv")
# 
# # Reduction from week 1 to week 6
# df_reduction_w1w6 <- df_weekly_attempts %>%
#   filter(study_week %in% c(1, 6)) %>%
#   pivot_wider(names_from = study_week, values_from = c(mean_initial, n_users),
#               names_glue = "{.value}_w{study_week}") %>%
#   mutate(
#     absolute_reduction = round(mean_attempted_w1 - mean_attempted_w6, 2),
#     relative_reduction = round((mean_attempted_w1 - mean_attempted_w6) / mean_attempted_w1 * 100, 1)
#   )
# 
# print(df_reduction_w1w6)
# write_csv(df_reduction_w1w6, "../reports/results_rq2_effectiveness/reduction_w1_to_w6.csv")

```

# Word tables

```{r}

doc <- read_docx() %>%
  body_add_par("RQ2.1: NB Regression — Dismissed Openings (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_1) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_1 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("RQ2.2: NB Regression — Initial App Opening Attempts (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_2) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_2 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit())

print(doc, target = "../reports/results_rq2_effectiveness/results_rq2.docx")

```

# Non preregistered model: longitudinal binomial / NB GLMM

**Research question shift.** The preregistered RQ2.1 and RQ2.2 ask whether *condition assignment* affects week-6 outcomes — intention-to-treat (ITT) questions about the randomised arm. The non-preregistered models below reframe these to **dose-response** questions: does the *current delay length* (in seconds) affect the dismissal rate / weekly attempt count, with the trajectory unfolding over all 6 weeks? This is a different scientific question — does the delay dose itself drive behaviour, regardless of which condition produced it — and complements rather than replaces the preregistered ITT analysis above. 

**Why move away from the week-6-only spec.** Three problems with the preregistered week-6 cross-sectional models:

1. **Selection / collider bias.** Condition affects who reaches week 6 (RQ1 is precisely about this). Restricting RQ2 to completers makes the week-6 cohort non-comparable across conditions, biasing the condition effect in an unknown direction. No covariate adjustment in the week-6 model fixes this — the bias is baked into the design choice to analyze week 6 alone.
2. **Post-treatment offset (RQ2.1).** `attempted_w6` is itself an outcome influenced by condition (it is the outcome of RQ2.2). Using it as an offset conditions on a downstream variable. The rate ratio for `condition` then has a slippery interpretation: "dismissals per attempt, holding attempts fixed at whatever they happened to be in this condition."
3. **Wasted information.** Weeks 2–5 are discarded entirely.

**Why a GLMM on weekly counts.** The model uses all 6 weeks, with a random intercept per participant to share strength without conditioning on completion. Participants who drop out simply contribute fewer rows; under MAR-style dropout assumptions, the estimator does not need a completers-only restriction. The binomial spec is the natural one for "successes/trials" — no offset needed.

**Why `delay_secs` instead of `condition`.** Using the time-varying current delay length (3s/6s/10s) operationalises the dose-response question directly. This is more sensitive than a 3-df condition contrast for two reasons: it uses 1 df, and because ABC/ACC/BCC participants experience multiple delays over the study, every such participant partially serves as their own control. The within-subject identification here is much stronger than in RQ1's hazard model — within-subject contrasts (e.g. an ABC participant at 3s in week 1 vs the same participant at 10s in week 5) directly identify the dose effect.

```{r}

# Weekly file: one row per participant × at-risk week (1..last_week).
# Weeks where the participant was active but had no events of the relevant
# type are explicit zeros; weeks past last_week are absent (post-dropout).
weekly <- read_csv("../data/processed/data_processed_behavioral_data_weekly.csv",
                   show_col_types = FALSE) %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

cat("Person-weeks:", nrow(weekly),
    "\nUnique participants:", n_distinct(weekly$participant_id), "\n")

```

## RQ2.1 analogue: dismissal rate trajectory

Binomial spec models the proportion of attempts dismissed. Weeks with
`attempted == 0` carry no information about the dismissal *rate* and are
excluded — they would force `0/0` cells.

```{r}

m_dismiss <- glmer(
  cbind(dismissed, attempted - dismissed) ~ delay_secs * study_week + (1 | participant_id),
  family  = binomial,
  data    = filter(weekly, attempted > 0),
  control = glmerControl(optimizer = "bobyqa")
)
summary(m_dismiss)

# Fixed-effect coefficient table. Binomial GLMM → exponentiated coefficients
# are odds ratios (per second of delay, per week, and the interaction).
results_glmm_dismiss <- broom.mixed::tidy(m_dismiss,
                                          effects       = "fixed",
                                          exponentiate  = TRUE,
                                          conf.int      = TRUE) %>%
  mutate(
    OR = round(estimate, 3),
    CI = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p  = case_when(p.value < .001 ~ "< .001",
                   TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, OR, `95% CI` = CI, p)

results_glmm_dismiss |> kable() |> kable_classic()

write_csv(results_glmm_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss_results.csv")
write_rds(m_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss.rds")

# Dose slope by week (emtrends).
# Because of the delay_secs × study_week interaction, the per-second dose
# effect varies by week. This reports the slope at week 1, mid-study, and
# week 6, exponentiated to "OR per second of delay".
em_slopes_dismiss <- emtrends(
  m_dismiss, ~ study_week,
  var = "delay_secs",
  at  = list(study_week = c(1, 3, 6))
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    OR_per_sec = signif(exp(delay_secs.trend), 3),
    CI         = paste0("[", signif(exp(asymp.LCL), 3), ", ",
                              signif(exp(asymp.UCL), 3), "]"),
    p          = case_when(p.value < .001 ~ "< .001",
                           TRUE           ~ as.character(round(p.value, 3)))
  ) |>
  dplyr::select(`Study week`         = study_week,
                `OR per sec of delay` = OR_per_sec,
                `95% CI`              = CI,
                p)

em_slopes_dismiss |> kable() |> kable_classic()
write_csv(em_slopes_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss_slopes.csv")

# Predicted dismissal probability at specific (delay, week) combinations.
# Easier to interpret than OR-per-second: gives the absolute dismissal rate
# the model expects for a typical participant at each grid point.
em_pred_dismiss <- emmeans(
  m_dismiss, ~ delay_secs * study_week,
  at   = list(delay_secs = c(3, 6, 10), study_week = c(1, 3, 6)),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Pr(dismiss)` = signif(prob, 3),
    `95% CI`      = paste0("[", signif(asymp.LCL, 3), ", ",
                                signif(asymp.UCL, 3), "]")
  ) |>
  dplyr::select(`Delay (s)`  = delay_secs,
                `Study week` = study_week,
                `Pr(dismiss)`,
                `95% CI`)

em_pred_dismiss |> kable() |> kable_classic()
write_csv(em_pred_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss_predicted.csv")

# # Predicted dismissal-rate trajectory: one line per delay, all 6 weeks.
# # Ribbons are 95% CIs.
# plot_data_dismiss <- emmeans(
#   m_dismiss, ~ delay_secs * study_week,
#   at   = list(delay_secs = c(3, 6, 10), study_week = 1:6),
#   type = "response"
# ) |>
#   summary() |>
#   as_tibble() |>
#   mutate(`Delay (s)` = factor(delay_secs))
# 
# p_dismiss <- ggplot(plot_data_dismiss,
#                     aes(study_week, prob,
#                         colour = `Delay (s)`, fill = `Delay (s)`,
#                         group  = `Delay (s)`)) +
#   geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
#               alpha = 0.15, colour = NA) +
#   geom_line(linewidth = 1) +
#   geom_point() +
#   scale_x_continuous(breaks = 1:6) +
#   labs(x = "Study week", y = "Predicted dismissal probability") +
#   theme_linedraw()
# 
# p_dismiss
# 
# ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_trajectory.png",
#        p_dismiss, width = 6, height = 4, dpi = 150)

# Companion: condition-level trajectory.
# The dose-response model above evaluates the linear (delay × week) surface
# at combinations that don't all occur in the data (e.g., 3s at week 6,
# which no condition reaches). The condition-level model below replaces
# `delay_secs` with `condition`, so each predicted line corresponds to one
# of the four randomised arms — the predictions stay inside the design,
# no extrapolation beyond observed (delay × week) cells.
m_dismiss_cond <- glmmTMB(
  cbind(dismissed, attempted - dismissed) ~ condition * study_week + (1 | participant_id),
  family = binomial,
  data   = filter(weekly, attempted > 0)
)
summary(m_dismiss_cond)

plot_data_dismiss_cond <- emmeans(
  m_dismiss_cond, ~ condition * study_week,
  at   = list(study_week = 1:6),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  rename_with(~ "ci_lower", any_of(c("asymp.LCL", "lower.CL"))) |>
  rename_with(~ "ci_upper", any_of(c("asymp.UCL", "upper.CL")))

p_dismiss_cond <- ggplot(plot_data_dismiss_cond,
                         aes(study_week, prob,
                             colour = condition, fill = condition,
                             group  = condition)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper),
              alpha = 0.2, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted dismissal probability",
       colour = "Condition", fill = "Condition") +
  theme_linedraw()

p_dismiss_cond

ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_trajectory_by_condition.png",
       p_dismiss_cond, width = 6, height = 4, dpi = 150)

# Companion: dose-response trajectory restricted to observed cells.
# Same predictions as the original dose-response plot, but masked to the
# (delay × week) combinations that actually occurred in the design.
# The 3s line shows weeks 1–2 only; 6s shows weeks 1–4; 10s spans all 6.
# This is the honest dose-response view — no late-week 3s extrapolation.
observed_cells <- weekly |> distinct(delay_secs, study_week)

plot_data_dismiss_obs <- plot_data_dismiss |>
  semi_join(observed_cells, by = c("delay_secs", "study_week"))

p_dismiss_obs <- ggplot(plot_data_dismiss_obs,
                        aes(study_week, prob,
                            colour = `Delay (s)`, fill = `Delay (s)`,
                            group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted dismissal probability") +
  theme_linedraw()

p_dismiss_obs

ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_trajectory_observed.png",
       p_dismiss_obs, width = 6, height = 4, dpi = 150)

```

- Hypothesis test provided by the delay_secs parameter.


## RQ2.2 analogue: weekly attempt count trajectory

NB on raw counts: a week with 0 attempts is a meaningful outcome ("this person
didn't try to open the app at all"), so the full weekly file is used (no
`attempted > 0` filter).

```{r}

# Centering predictors before fitting.
# Without centering, glmer.nb fails to converge with "very large eigenvalue
# – rescale variables". The interaction delay_secs * study_week has range
# 3..60, an order of magnitude larger than the main effects, which makes
# the design matrix poorly conditioned and trips up glmer.nb's outer-loop
# optimisation of the dispersion parameter theta.
# Centering at the mean fixes the conditioning problem. The interaction
# coefficient is unchanged; the main effects are now interpreted at the
# *mean* of the other predictor (i.e. the dose effect at mid-study, and
# the time trend at mean dose), which is also more substantively useful
# than "at zero" — week 0 and 0s delay are both outside the data.
delay_mean <- mean(weekly$delay_secs)
week_mean  <- mean(weekly$study_week)

weekly_c <- weekly |>
  mutate(
    delay_secs_c = delay_secs - delay_mean,
    study_week_c = study_week - week_mean
  )

# m_attempts <- glmer.nb(
#   attempted ~ delay_secs_c * study_week_c + (1 | participant_id),
#   data    = weekly_c,
#   control = glmerControl(optimizer = "bobyqa",
#                          optCtrl = list(maxfun = 2e5))
# )

m_attempts <- glmmTMB(
  attempted ~ delay_secs_c * study_week_c + (1 | participant_id),
  data   = weekly_c,
  family = nbinom2
)
summary(m_attempts)

# Fixed-effect coefficient table. NB GLMM with log link → exponentiated
# coefficients are rate ratios. With centring:
#   delay_secs_c           = dose effect at mean week (~3.5)
#   study_week_c           = time trend at mean delay
#   delay_secs_c:study_week_c = interaction (unchanged by centring)
results_glmm_attempts <- broom.mixed::tidy(m_attempts,
                                           effects       = "fixed",
                                           exponentiate  = TRUE,
                                           conf.int      = TRUE) %>%
  mutate(
    RR = round(estimate, 3),
    CI = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p  = case_when(p.value < .001 ~ "< .001",
                   TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p)

results_glmm_attempts |> kable() |> kable_classic()

write_csv(results_glmm_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts_results.csv")
write_rds(m_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts.rds")

# Dose slope by week (emtrends), reported on the original week scale.
# emtrends is evaluated at centred week values corresponding to weeks 1, 3,
# 6 on the original scale; the displayed `Study week` column adds the mean
# back so the table is interpretable.
em_slopes_attempts <- emtrends(
  m_attempts, ~ study_week_c,
  var = "delay_secs_c",
  at  = list(study_week_c = c(1, 3, 6) - week_mean)
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Study week` = study_week_c + week_mean,
    RR_per_sec   = signif(exp(delay_secs_c.trend), 3),
    CI           = paste0("[", signif(exp(asymp.LCL), 3), ", ",
                                signif(exp(asymp.UCL), 3), "]"),
    p            = case_when(p.value < .001 ~ "< .001",
                             TRUE           ~ as.character(round(p.value, 3)))
  ) |>
  dplyr::select(`Study week`,
                `RR per sec of delay` = RR_per_sec,
                `95% CI`              = CI,
                p)

em_slopes_attempts |> kable() |> kable_classic()
write_csv(em_slopes_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts_slopes.csv")

# Predicted weekly attempt count at specific (delay, week) combinations.
# Model uses centred predictors, so convert original-scale grid points to
# the centred scale before passing to emmeans, then convert back for display.
em_pred_attempts <- emmeans(
  m_attempts, ~ delay_secs_c * study_week_c,
  at   = list(
    delay_secs_c = c(3, 6, 10) - delay_mean,
    study_week_c = c(1, 3, 6) - week_mean
  ),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Delay (s)`     = delay_secs_c + delay_mean,
    `Study week`    = study_week_c + week_mean,
    `Mean attempts` = signif(response, 3),
    `95% CI`        = paste0("[", signif(asymp.LCL, 3), ", ",
                                  signif(asymp.UCL, 3), "]")
  ) |>
  dplyr::select(`Delay (s)`, `Study week`, `Mean attempts`, `95% CI`)

em_pred_attempts |> kable() |> kable_classic()
write_csv(em_pred_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts_predicted.csv")

# # Predicted weekly-attempt trajectory: one line per delay, all 6 weeks.
# # Ribbons are 95% CIs. Predictors are on the centred scale internally;
# # convert back to original scale for the plot axes.
# plot_data_attempts <- emmeans(
#   m_attempts, ~ delay_secs_c * study_week_c,
#   at   = list(
#     delay_secs_c = c(3, 6, 10) - delay_mean,
#     study_week_c = (1:6) - week_mean
#   ),
#   type = "response"
# ) |>
#   summary() |>
#   as_tibble() |>
#   mutate(
#     `Delay (s)` = factor(delay_secs_c + delay_mean),
#     study_week  = study_week_c + week_mean
#   )
# 
# p_attempts <- ggplot(plot_data_attempts,
#                      aes(study_week, response,
#                          colour = `Delay (s)`, fill = `Delay (s)`,
#                          group  = `Delay (s)`)) +
#   geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
#               alpha = 0.15, colour = NA) +
#   geom_line(linewidth = 1) +
#   geom_point() +
#   scale_x_continuous(breaks = 1:6) +
#   labs(x = "Study week", y = "Predicted weekly attempts") +
#   theme_linedraw()
# 
# p_attempts
# 
# ggsave("../reports/results_rq2_effectiveness/glmm_attempts_trajectory.png",
#        p_attempts, width = 6, height = 4, dpi = 150)

# Companion: condition-level trajectory.
# Same logic as the dismissal companion — predicting per condition keeps
# every plotted (delay × week) point inside the actual design.
m_attempts_cond <- glmmTMB(
  attempted ~ condition * study_week_c + (1 | participant_id),
  data   = weekly_c,
  family = nbinom2
)
summary(m_attempts_cond)

plot_data_attempts_cond <- emmeans(
  m_attempts_cond, ~ condition * study_week_c,
  at   = list(study_week_c = (1:6) - week_mean),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  rename_with(~ "ci_lower", any_of(c("asymp.LCL", "lower.CL"))) |>
  rename_with(~ "ci_upper", any_of(c("asymp.UCL", "upper.CL"))) |>
  mutate(study_week = study_week_c + week_mean)

p_attempts_cond <- ggplot(plot_data_attempts_cond,
                          aes(study_week, response,
                              colour = condition, fill = condition,
                              group  = condition)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper),
              alpha = 0.2, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted weekly attempts",
       colour = "Condition", fill = "Condition") +
  theme_linedraw()

p_attempts_cond

ggsave("../reports/results_rq2_effectiveness/glmm_attempts_trajectory_by_condition.png",
       p_attempts_cond, width = 6, height = 4, dpi = 150)

# Companion: dose-response trajectory restricted to observed cells.
# Same logic as the dismissal version. The model uses centred predictors,
# so recover the original-scale delay column for the semi_join.
plot_data_attempts_obs <- plot_data_attempts |>
  mutate(delay_secs = delay_secs_c + delay_mean) |>
  semi_join(observed_cells, by = c("delay_secs", "study_week"))

p_attempts_obs <- ggplot(plot_data_attempts_obs,
                         aes(study_week, response,
                             colour = `Delay (s)`, fill = `Delay (s)`,
                             group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted weekly attempts") +
  theme_linedraw()

p_attempts_obs

ggsave("../reports/results_rq2_effectiveness/glmm_attempts_trajectory_observed.png",
       p_attempts_obs, width = 6, height = 4, dpi = 150)

```



# Session info

```{r}
sessionInfo()
```
