---
title: "RQ2: Effectiveness"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- replace analyses with MLE/multilevel models for proper ITT?
- check i understand and have implementd 2.1 and 2.2 correctly

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(MASS)
library(broom)
library(emmeans)
library(flextable)
library(officer)
library(AER)

dir.create("../reports/", showWarnings = FALSE)
dir.create("../reports/results_rq2_effectiveness/")

```

# Load data

```{r}

df_rq2 <- read_csv("../data/processed/data_processed_behavioral_data_open_attempts.csv") %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

```

# RQ 2.1: Dismissed app openings in week 6

Model: NB regression, offset = log(attempted_w6). Covariates: dismissed_w1, attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_21 <- glm(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1,
  offset = log(attempted_w6),
  data   = df_rq2,
  family = poisson()
)
disp_test_21 <- dispersiontest(poisson_21)
cat("RQ2.1 dispersion test:", capture.output(print(disp_test_21)), sep = "\n")

zero_pct_21 <- mean(df_rq2$dismissed_w6 == 0, na.rm = TRUE) * 100
cat(sprintf("RQ2.1 zero proportion: %.1f%%\n", zero_pct_21))

```

## Main model

```{r}

model_rq2_1 <- glm.nb(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1 + offset(log(attempted_w6)),
  data = df_rq2
)

summary(model_rq2_1)

results_rq2_1 <- tidy(model_rq2_1, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p) 

results_rq2_1

write_csv(results_rq2_1, "../reports/results_rq2_effectiveness/model_rq2_1_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_1 <- emmeans(model_rq2_1, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq2_1

write_csv(pairwise_rq2_1, "../reports/results_rq2_effectiveness/pairwise_rq2_1.csv")

```

## Relative reduction: % dismissed of attempted per condition × week

```{r}

# TODO

```

# RQ 2.2: Initial app opening attempts in week 6

Model: NB regression, covariate = attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_22 <- glm(
  attempted_w6 ~ condition + attempted_w1,
  data   = df_rq2,
  family = poisson()
)
disp_test_22 <- dispersiontest(poisson_22)
cat("\nRQ2.2 dispersion test:", capture.output(print(disp_test_22)), sep = "\n")

zero_pct_22 <- mean(df_rq2$attempted_w6 == 0, na.rm = TRUE) * 100
cat(sprintf("RQ2.2 zero proportion: %.1f%%\n", zero_pct_22))

```

## Main model

```{r}

model_rq2_2 <- glm.nb(
  attempted_w6 ~ condition + attempted_w1,
  data = df_rq2
)

summary(model_rq2_2)

results_rq2_2 <- tidy(model_rq2_2, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p) 

results_rq2_2

write_csv(results_rq2_2, "../reports/results_rq2_effectiveness/model_rq2_2_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_2 <- emmeans(model_rq2_2, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq2_2

write_csv(pairwise_rq2_2, "../reports/results_rq2_effectiveness/pairwise_rq2_2.csv")

```

## Mean initial attempts per user per condition × week

```{r}

# TODO
#
# df_weekly_attempts <- df_rq2_event %>%
#   group_by(participant_id, condition, study_week) %>%
#   summarise(initial = sum(initial_attempt), .groups = "drop") %>%
#   group_by(condition, study_week) %>%
#   summarise(
#     n_users      = n(),
#     mean_initial = round(mean(initial), 2),
#     .groups = "drop"
#   )
# 
# df_weekly_attempts
# 
# write_csv(df_weekly_attempts, "../reports/results_rq2_effectiveness/weekly_attempts_by_condition.csv")
# 
# # Reduction from week 1 to week 6
# df_reduction_w1w6 <- df_weekly_attempts %>%
#   filter(study_week %in% c(1, 6)) %>%
#   pivot_wider(names_from = study_week, values_from = c(mean_initial, n_users),
#               names_glue = "{.value}_w{study_week}") %>%
#   mutate(
#     absolute_reduction = round(mean_attempted_w1 - mean_attempted_w6, 2),
#     relative_reduction = round((mean_attempted_w1 - mean_attempted_w6) / mean_attempted_w1 * 100, 1)
#   )
# 
# print(df_reduction_w1w6)
# write_csv(df_reduction_w1w6, "../reports/results_rq2_effectiveness/reduction_w1_to_w6.csv")

```

# Word tables

```{r}

doc <- read_docx() %>%
  body_add_par("RQ2.1: NB Regression — Dismissed Openings (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_1) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_1 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("RQ2.2: NB Regression — Initial App Opening Attempts (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_2) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_2 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit())

print(doc, target = "../reports/results_rq2_effectiveness/results_rq2.docx")

```

# Session info

```{r}
sessionInfo()
```
