---
title: "RQ2: Effectiveness and Efficacy"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Note on Terminology

**Efficacy vs. Effectiveness:** The preregistered analyses (RQ2.1 and RQ2.2) are restricted to completers — participants with activity in both Week 1 and Week 6 — measuring *efficacy* (intervention effects under controlled conditions). The exploratory GLMM models use the full weekly dataset with all participants who had any activity, approximating intention-to-treat and measuring *effectiveness* (real-world intervention effects).

# TODO

- check i understand and have implemented 2.1 and 2.2 correctly

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(MASS)
library(broom)
library(broom.mixed)
library(emmeans)
library(flextable)
library(officer)
library(AER)
library(lme4)
library(glmmTMB)
library(knitr)
library(kableExtra)

dir.create("../reports/", showWarnings = FALSE)
dir.create("../reports/results_rq2_effectiveness/")

```

# Load data

```{r}

df_rq2 <- read_csv("../data/processed/data_processed_behavioral_data_open_attempts.csv") %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

```

# RQ 2.1: Dismissed app openings in week 6

Model: NB regression, offset = log(attempted_w6). Covariates: dismissed_w1, attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_21 <- glm(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1,
  offset = log(attempted_w6),
  data   = df_rq2,
  family = poisson()
)
disp_test_21 <- dispersiontest(poisson_21)
cat("RQ2.1 dispersion test:", capture.output(print(disp_test_21)), sep = "\n")

zero_pct_21 <- mean(df_rq2$dismissed_w6 == 0, na.rm = TRUE) * 100
cat(sprintf("RQ2.1 zero proportion: %.1f%%\n", zero_pct_21))

```

## Main model

```{r}

model_rq2_1 <- glm.nb(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1 + offset(log(attempted_w6)),
  data = df_rq2
)

summary(model_rq2_1)

results_rq2_1 <- tidy(model_rq2_1, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p) 

results_rq2_1 |> kable() |> kable_classic()

write_csv(results_rq2_1, "../reports/results_rq2_effectiveness/model_rq2_1_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_1 <- emmeans(model_rq2_1, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq2_1 |> kable() |> kable_classic()

write_csv(pairwise_rq2_1, "../reports/results_rq2_effectiveness/pairwise_rq2_1.csv")

```

## Estimated marginal means: predicted dismissal rate per condition

```{r}

condition_order <- c("ABC", "ACC", "BCC", "CCC")

em_pred_rq2_1 <- emmeans(model_rq2_1, ~ condition, type = "response") |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(condition = factor(condition, levels = condition_order)) |>
  arrange(condition)

em_pred_rq2_1_table <- em_pred_rq2_1 |>
  mutate(
    `95% CI` = paste0("[", signif(asymp.LCL, 3), ", ", signif(asymp.UCL, 3), "]"),
    across(where(is.numeric), ~ round(.x, 3))
  ) |>
  dplyr::select(Condition = condition, `Dismissals per attempt` = response, SE, `95% CI`)

em_pred_rq2_1_table |> kable() |> kable_classic()

write_csv(em_pred_rq2_1_table, "../reports/results_rq2_effectiveness/emmeans_rq2_1.csv")

```

```{r}

p_em_rq2_1 <- ggplot(em_pred_rq2_1,
                     aes(x = condition, y = response, ymin = asymp.LCL, ymax = asymp.UCL)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0.2) +
  labs(x = "Condition", y = "Predicted dismissals per attempt",
       title = "RQ2.1: Estimated marginal means — dismissal rate by condition") +
  theme_linedraw()

p_em_rq2_1

ggsave("../reports/results_rq2_effectiveness/emmeans_rq2_1_plot.png",
       p_em_rq2_1, width = 5, height = 4, dpi = 150)

```

## Relative reduction: % dismissed of attempted per condition × week

```{r}

# TODO

```

# RQ 2.2: Initial app opening attempts in week 6

Model: NB regression, covariate = attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_22 <- glm(
  attempted_w6 ~ condition + attempted_w1,
  data   = df_rq2,
  family = poisson()
)
disp_test_22 <- dispersiontest(poisson_22)
cat("\nRQ2.2 dispersion test:", capture.output(print(disp_test_22)), sep = "\n")

zero_pct_22 <- mean(df_rq2$attempted_w6 == 0, na.rm = TRUE) * 100
cat(sprintf("RQ2.2 zero proportion: %.1f%%\n", zero_pct_22))

```

## Main model

```{r}

model_rq2_2 <- glm.nb(
  attempted_w6 ~ condition + attempted_w1,
  data = df_rq2
)

summary(model_rq2_2)

results_rq2_2 <- tidy(model_rq2_2, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p) 

results_rq2_2 |> kable() |> kable_classic()

write_csv(results_rq2_2, "../reports/results_rq2_effectiveness/model_rq2_2_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_2 <- emmeans(model_rq2_2, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

pairwise_rq2_2 |> kable() |> kable_classic()

write_csv(pairwise_rq2_2, "../reports/results_rq2_effectiveness/pairwise_rq2_2.csv")

```

## Estimated marginal means: predicted attempt count per condition

```{r}

em_pred_rq2_2 <- emmeans(model_rq2_2, ~ condition, type = "response") |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(condition = factor(condition, levels = condition_order)) |>
  arrange(condition)

em_pred_rq2_2_table <- em_pred_rq2_2 |>
  mutate(
    `95% CI` = paste0("[", signif(asymp.LCL, 3), ", ", signif(asymp.UCL, 3), "]"),
    across(where(is.numeric), ~ round(.x, 3))
  ) |>
  dplyr::select(Condition = condition, `Mean attempts` = response, SE, `95% CI`)

em_pred_rq2_2_table |> kable() |> kable_classic()

write_csv(em_pred_rq2_2_table, "../reports/results_rq2_effectiveness/emmeans_rq2_2.csv")

```

```{r}

p_em_rq2_2 <- ggplot(em_pred_rq2_2,
                     aes(x = condition, y = response, ymin = asymp.LCL, ymax = asymp.UCL)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0.2) +
  labs(x = "Condition", y = "Predicted weekly attempts",
       title = "RQ2.2: Estimated marginal means — attempt count by condition") +
  theme_linedraw()

p_em_rq2_2

ggsave("../reports/results_rq2_effectiveness/emmeans_rq2_2_plot.png",
       p_em_rq2_2, width = 5, height = 4, dpi = 150)

```

## Mean initial attempts per user per condition × week

```{r}

# TODO
#
# df_weekly_attempts <- df_rq2_event %>%
#   group_by(participant_id, condition, study_week) %>%
#   summarise(initial = sum(initial_attempt), .groups = "drop") %>%
#   group_by(condition, study_week) %>%
#   summarise(
#     n_users      = n(),
#     mean_initial = round(mean(initial), 2),
#     .groups = "drop"
#   )
# 
# df_weekly_attempts
# 
# write_csv(df_weekly_attempts, "../reports/results_rq2_effectiveness/weekly_attempts_by_condition.csv")
# 
# # Reduction from week 1 to week 6
# df_reduction_w1w6 <- df_weekly_attempts %>%
#   filter(study_week %in% c(1, 6)) %>%
#   pivot_wider(names_from = study_week, values_from = c(mean_initial, n_users),
#               names_glue = "{.value}_w{study_week}") %>%
#   mutate(
#     absolute_reduction = round(mean_attempted_w1 - mean_attempted_w6, 2),
#     relative_reduction = round((mean_attempted_w1 - mean_attempted_w6) / mean_attempted_w1 * 100, 1)
#   )
# 
# print(df_reduction_w1w6)
# write_csv(df_reduction_w1w6, "../reports/results_rq2_effectiveness/reduction_w1_to_w6.csv")

```

# Word tables

```{r}

doc <- read_docx() %>%
  body_add_par("RQ2.1: NB Regression — Dismissed Openings (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_1) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Estimated Marginal Means (predicted dismissal rate)", style = "heading 2") %>%
  body_add_flextable(flextable(em_pred_rq2_1_table) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_1 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("RQ2.2: NB Regression — Initial App Opening Attempts (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_2) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Estimated Marginal Means (predicted attempt count)", style = "heading 2") %>%
  body_add_flextable(flextable(em_pred_rq2_2_table) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_2 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit())

print(doc, target = "../reports/results_rq2_effectiveness/results_rq2.docx")

```

# Non preregistered model: longitudinal binomial / NB GLMM

**Research question shift.** The preregistered RQ2.1 and RQ2.2 ask whether *condition assignment* affects week-6 outcomes — intention-to-treat (ITT) questions about the randomised arm. The non-preregistered models below reframe these to **dose-response** questions: does the *current delay length* (in seconds) affect the dismissal rate / weekly attempt count, with the trajectory unfolding over all 6 weeks? This is a different scientific question — does the delay dose itself drive behaviour, regardless of which condition produced it — and complements rather than replaces the preregistered ITT analysis above. 

**Why move away from the week-6-only spec.** Three problems with the preregistered week-6 cross-sectional models:

1. **Selection / collider bias.** Condition affects who reaches week 6 (RQ1 is precisely about this). Restricting RQ2 to completers makes the week-6 cohort non-comparable across conditions, biasing the condition effect in an unknown direction. No covariate adjustment in the week-6 model fixes this — the bias is baked into the design choice to analyze week 6 alone.
2. **Post-treatment offset (RQ2.1).** `attempted_w6` is itself an outcome influenced by condition (it is the outcome of RQ2.2). Using it as an offset conditions on a downstream variable. The rate ratio for `condition` then has a slippery interpretation: "dismissals per attempt, holding attempts fixed at whatever they happened to be in this condition."
3. **Wasted information.** Weeks 2–5 are discarded entirely.

**Why a GLMM on weekly counts.** The model uses all 6 weeks, with a random intercept per participant to share strength without conditioning on completion. Participants who drop out simply contribute fewer rows; under MAR-style dropout assumptions, the estimator does not need a completers-only restriction. The binomial spec is the natural one for "successes/trials" — no offset needed.

**Why `delay_secs` instead of `condition`.** Using the time-varying current delay length (3s/6s/10s) operationalises the dose-response question directly. This is more sensitive than a 3-df condition contrast for two reasons: it uses 1 df, and because ABC/ACC/BCC participants experience multiple delays over the study, every such participant partially serves as their own control. The within-subject identification here is much stronger than in RQ1's hazard model — within-subject contrasts (e.g. an ABC participant at 3s in week 1 vs the same participant at 10s in week 5) directly identify the dose effect.

```{r}

# Weekly file: one row per participant × at-risk week (1..last_week).
# Weeks where the participant was active but had no events of the relevant
# type are explicit zeros; weeks past last_week are absent (post-dropout).
weekly <- read_csv("../data/processed/data_processed_behavioral_data_weekly.csv",
                   show_col_types = FALSE) %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

cat("Person-weeks:", nrow(weekly),
    "\nUnique participants:", n_distinct(weekly$participant_id), "\n")

```

## RQ2.1 analogue: dismissal rate trajectory

Binomial spec models the proportion of attempts dismissed. Weeks with
`attempted == 0` carry no information about the dismissal *rate* and are
excluded — they would force `0/0` cells.

```{r}

# Centre predictors so the main-effect coefficients are interpretable at
# the mean of the other predictor (otherwise the `delay_secs` main effect
# would be the slope at study_week = 0, which is outside the data). Matches
# the parameterisation used by m_attempts below.
delay_mean <- mean(weekly$delay_secs)
week_mean  <- mean(weekly$study_week)

weekly_dismiss_c <- weekly |>
  filter(attempted > 0) |>
  mutate(
    delay_secs_c = delay_secs - delay_mean,
    study_week_c = study_week - week_mean
  )

m_dismiss <- glmer(
  cbind(dismissed, attempted - dismissed) ~ delay_secs_c * study_week_c + (1 | participant_id),
  family  = binomial,
  data    = weekly_dismiss_c,
  control = glmerControl(optimizer = "bobyqa")
)
summary(m_dismiss)

# Fixed-effect coefficient table. Binomial GLMM → exponentiated coefficients
# are odds ratios. With centring:
#   delay_secs_c              = per-second dose effect at mean week
#   study_week_c              = time trend at mean delay
#   delay_secs_c:study_week_c = interaction (unchanged by centring)
results_glmm_dismiss <- broom.mixed::tidy(m_dismiss,
                                          effects       = "fixed",
                                          exponentiate  = TRUE,
                                          conf.int      = TRUE) %>%
  mutate(
    OR = round(estimate, 3),
    CI = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p  = case_when(p.value < .001 ~ "< .001",
                   TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, OR, `95% CI` = CI, p)

results_glmm_dismiss |> kable() |> kable_classic()

write_csv(results_glmm_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss_results.csv")
write_rds(m_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss.rds")

# Dose slope by week (emtrends), reported on the original week scale.
# emtrends is evaluated at centred week values corresponding to weeks 1, 3,
# 6 on the original scale; the displayed `Study week` column adds the mean
# back so the table is interpretable.
em_slopes_dismiss <- emtrends(
  m_dismiss, ~ study_week_c,
  var = "delay_secs_c",
  at  = list(study_week_c = c(1, 3, 6) - week_mean)
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Study week` = study_week_c + week_mean,
    OR_per_sec   = signif(exp(delay_secs_c.trend), 3),
    CI           = paste0("[", signif(exp(asymp.LCL), 3), ", ",
                                signif(exp(asymp.UCL), 3), "]"),
    p            = case_when(p.value < .001 ~ "< .001",
                             TRUE           ~ as.character(round(p.value, 3)))
  ) |>
  dplyr::select(`Study week`,
                `OR per sec of delay` = OR_per_sec,
                `95% CI`              = CI,
                p)

em_slopes_dismiss |> kable() |> kable_classic()
write_csv(em_slopes_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss_slopes.csv")

# Predicted dismissal probability at specific (delay, week) combinations.
# Model uses centred predictors, so convert original-scale grid points to
# the centred scale before passing to emmeans, then convert back for display.
em_pred_dismiss <- emmeans(
  m_dismiss, ~ delay_secs_c * study_week_c,
  at   = list(
    delay_secs_c = c(3, 6, 10) - delay_mean,
    study_week_c = c(1, 3, 6) - week_mean
  ),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Delay (s)`   = delay_secs_c + delay_mean,
    `Study week`  = study_week_c + week_mean,
    `Pr(dismiss)` = signif(prob, 3),
    `95% CI`      = paste0("[", signif(asymp.LCL, 3), ", ",
                                signif(asymp.UCL, 3), "]")
  ) |>
  dplyr::select(`Delay (s)`, `Study week`, `Pr(dismiss)`, `95% CI`)

em_pred_dismiss |> kable() |> kable_classic()
write_csv(em_pred_dismiss,
          "../reports/results_rq2_effectiveness/glmm_dismiss_predicted.csv")

# Full grid of predictions on original scale (needed to filter to observed cells below).
plot_data_dismiss <- emmeans(
  m_dismiss, ~ delay_secs_c * study_week_c,
  at   = list(
    delay_secs_c = c(3, 6, 10) - delay_mean,
    study_week_c = (1:6) - week_mean
  ),
  type = "response"
) |>
  summary() |>
  as_tibble() |>
  mutate(
    `Delay (s)` = factor(delay_secs_c + delay_mean),
    delay_secs  = delay_secs_c + delay_mean,
    study_week  = study_week_c + week_mean
  )

# Companion: condition-level trajectory.
# The dose-response model above evaluates the linear (delay × week) surface
# at combinations that don't all occur in the data (e.g., 3s at week 6,
# which no condition reaches). The condition-level model below replaces
# `delay_secs` with `condition`, so each predicted line corresponds to one
# of the four randomised arms — the predictions stay inside the design,
# no extrapolation beyond observed (delay × week) cells.
m_dismiss_cond <- glmmTMB(
  cbind(dismissed, attempted - dismissed) ~ condition * study_week + (1 | participant_id),
  family = binomial,
  data   = filter(weekly, attempted > 0)
)
summary(m_dismiss_cond)

plot_data_dismiss_cond <- emmeans(
  m_dismiss_cond, ~ condition * study_week,
  at   = list(study_week = 1:6),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  rename_with(~ "ci_lower", any_of(c("asymp.LCL", "lower.CL"))) |>
  rename_with(~ "ci_upper", any_of(c("asymp.UCL", "upper.CL")))

p_dismiss_cond <- ggplot(plot_data_dismiss_cond,
                         aes(study_week, prob,
                             colour = condition, fill = condition,
                             group  = condition)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper),
              alpha = 0.2, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted dismissal probability",
       colour = "Condition", fill = "Condition") +
  theme_linedraw()

p_dismiss_cond

ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_trajectory_by_condition.png",
       p_dismiss_cond, width = 6, height = 4, dpi = 150)

# Dose-response trajectory restricted to observed (delay × week) cells.
# 3s shown for weeks 1–2 only; 6s for weeks 1–4; 10s for all 6 weeks.
observed_cells <- weekly |> distinct(delay_secs, study_week)

plot_data_dismiss_obs <- plot_data_dismiss |>
  semi_join(observed_cells, by = c("delay_secs", "study_week"))

p_dismiss_obs <- ggplot(plot_data_dismiss_obs,
                        aes(study_week, prob,
                            colour = `Delay (s)`, fill = `Delay (s)`,
                            group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted dismissal probability",
       colour = "Delay (s)", fill = "Delay (s)") +
  theme_linedraw()

p_dismiss_obs

ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_trajectory_observed.png",
       p_dismiss_obs, width = 6, height = 4, dpi = 150)

# Full-grid dose-response trajectory: all delay × week combinations including
# those that never occurred in the study (e.g. 3s at week 6). Extrapolation
# beyond the design, so interpret with caution — but shows the model's full
# implied surface.
p_dismiss_full <- ggplot(plot_data_dismiss,
                         aes(study_week, prob,
                             colour = `Delay (s)`, fill = `Delay (s)`,
                             group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted dismissal probability",
       colour = "Delay (s)", fill = "Delay (s)",
       caption = "All delay × week combinations shown, including counterfactual cells") +
  theme_linedraw()

p_dismiss_full

ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_trajectory_full.png",
       p_dismiss_full, width = 6, height = 4, dpi = 150)

# EMMs at Week 6 only — same format as preregistered EMM plot.
condition_order <- c("ABC", "ACC", "BCC", "CCC")

em_dismiss_w6 <- plot_data_dismiss_cond |>
  filter(study_week == 6) |>
  mutate(condition = factor(condition, levels = condition_order)) |>
  arrange(condition)

p_dismiss_w6 <- ggplot(em_dismiss_w6,
                       aes(x = condition, y = prob,
                           ymin = ci_lower, ymax = ci_upper)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0.2) +
  labs(x = "Condition", y = "Predicted dismissal probability (Week 6)",
       title = "RQ2.1 (exploratory): EMMs at Week 6 — dismissal rate by condition") +
  theme_linedraw()

p_dismiss_w6

ggsave("../reports/results_rq2_effectiveness/glmm_dismiss_emm_w6.png",
       p_dismiss_w6, width = 5, height = 4, dpi = 150)

```

- Hypothesis test provided by the delay_secs parameter.


## RQ2.2 analogue: weekly attempt count trajectory

NB on raw counts: a week with 0 attempts is a meaningful outcome ("this person
didn't try to open the app at all"), so the full weekly file is used (no
`attempted > 0` filter).

```{r}

# delay_mean and week_mean were defined in the m_dismiss chunk above.
# Centring is also needed here for a separate reason: without it, glmer.nb
# fails to converge ("very large eigenvalue – rescale variables") because
# the interaction delay_secs * study_week has range 3..60, much larger
# than the main effects, leaving the design matrix poorly conditioned.
weekly_c <- weekly |>
  mutate(
    delay_secs_c = delay_secs - delay_mean,
    study_week_c = study_week - week_mean
  )

# m_attempts <- glmer.nb(
#   attempted ~ delay_secs_c * study_week_c + (1 | participant_id),
#   data    = weekly_c,
#   control = glmerControl(optimizer = "bobyqa",
#                          optCtrl = list(maxfun = 2e5))
# )

m_attempts <- glmmTMB(
  attempted ~ delay_secs_c * study_week_c + (1 | participant_id),
  data   = weekly_c,
  family = nbinom2
)
summary(m_attempts)

# Fixed-effect coefficient table. NB GLMM with log link → exponentiated
# coefficients are rate ratios. With centring:
#   delay_secs_c           = dose effect at mean week (~3.5)
#   study_week_c           = time trend at mean delay
#   delay_secs_c:study_week_c = interaction (unchanged by centring)
results_glmm_attempts <- broom.mixed::tidy(m_attempts,
                                           effects       = "fixed",
                                           exponentiate  = TRUE,
                                           conf.int      = TRUE) %>%
  mutate(
    RR = round(estimate, 3),
    CI = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p  = case_when(p.value < .001 ~ "< .001",
                   TRUE           ~ as.character(round(p.value, 3)))
  ) %>%
  dplyr::select(Predictor = term, `Rate Ratio` = RR, `95% CI` = CI, p)

results_glmm_attempts |> kable() |> kable_classic()

write_csv(results_glmm_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts_results.csv")
write_rds(m_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts.rds")

# Dose slope by week (emtrends), reported on the original week scale.
# emtrends is evaluated at centred week values corresponding to weeks 1, 3,
# 6 on the original scale; the displayed `Study week` column adds the mean
# back so the table is interpretable.
em_slopes_attempts <- emtrends(
  m_attempts, ~ study_week_c,
  var = "delay_secs_c",
  at  = list(study_week_c = c(1, 3, 6) - week_mean)
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Study week` = study_week_c + week_mean,
    RR_per_sec   = signif(exp(delay_secs_c.trend), 3),
    CI           = paste0("[", signif(exp(asymp.LCL), 3), ", ",
                                signif(exp(asymp.UCL), 3), "]"),
    p            = case_when(p.value < .001 ~ "< .001",
                             TRUE           ~ as.character(round(p.value, 3)))
  ) |>
  dplyr::select(`Study week`,
                `RR per sec of delay` = RR_per_sec,
                `95% CI`              = CI,
                p)

em_slopes_attempts |> kable() |> kable_classic()
write_csv(em_slopes_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts_slopes.csv")

# Predicted weekly attempt count at specific (delay, week) combinations.
# Model uses centred predictors, so convert original-scale grid points to
# the centred scale before passing to emmeans, then convert back for display.
em_pred_attempts <- emmeans(
  m_attempts, ~ delay_secs_c * study_week_c,
  at   = list(
    delay_secs_c = c(3, 6, 10) - delay_mean,
    study_week_c = c(1, 3, 6) - week_mean
  ),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    `Delay (s)`     = delay_secs_c + delay_mean,
    `Study week`    = study_week_c + week_mean,
    `Mean attempts` = signif(response, 3),
    `95% CI`        = paste0("[", signif(asymp.LCL, 3), ", ",
                                  signif(asymp.UCL, 3), "]")
  ) |>
  dplyr::select(`Delay (s)`, `Study week`, `Mean attempts`, `95% CI`)

em_pred_attempts |> kable() |> kable_classic()
write_csv(em_pred_attempts,
          "../reports/results_rq2_effectiveness/glmm_attempts_predicted.csv")

# Full grid of predictions on original scale (needed to filter to observed cells below).
plot_data_attempts <- emmeans(
  m_attempts, ~ delay_secs_c * study_week_c,
  at   = list(
    delay_secs_c = c(3, 6, 10) - delay_mean,
    study_week_c = (1:6) - week_mean
  ),
  type = "response"
) |>
  summary() |>
  as_tibble() |>
  mutate(
    `Delay (s)` = factor(delay_secs_c + delay_mean),
    delay_secs  = delay_secs_c + delay_mean,
    study_week  = study_week_c + week_mean
  )

# Companion: condition-level trajectory.
# Same logic as the dismissal companion — predicting per condition keeps
# every plotted (delay × week) point inside the actual design.
m_attempts_cond <- glmmTMB(
  attempted ~ condition * study_week_c + (1 | participant_id),
  data   = weekly_c,
  family = nbinom2
)
summary(m_attempts_cond)

plot_data_attempts_cond <- emmeans(
  m_attempts_cond, ~ condition * study_week_c,
  at   = list(study_week_c = (1:6) - week_mean),
  type = "response"
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  rename_with(~ "ci_lower", any_of(c("asymp.LCL", "lower.CL"))) |>
  rename_with(~ "ci_upper", any_of(c("asymp.UCL", "upper.CL"))) |>
  mutate(study_week = study_week_c + week_mean)

p_attempts_cond <- ggplot(plot_data_attempts_cond,
                          aes(study_week, response,
                              colour = condition, fill = condition,
                              group  = condition)) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper),
              alpha = 0.2, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted weekly attempts",
       colour = "Condition", fill = "Condition") +
  theme_linedraw()

p_attempts_cond

ggsave("../reports/results_rq2_effectiveness/glmm_attempts_trajectory_by_condition.png",
       p_attempts_cond, width = 6, height = 4, dpi = 150)

# Dose-response trajectory restricted to observed (delay × week) cells.
plot_data_attempts_obs <- plot_data_attempts |>
  semi_join(observed_cells, by = c("delay_secs", "study_week"))

p_attempts_obs <- ggplot(plot_data_attempts_obs,
                         aes(study_week, response,
                             colour = `Delay (s)`, fill = `Delay (s)`,
                             group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted weekly attempts",
       colour = "Delay (s)", fill = "Delay (s)") +
  theme_linedraw()

p_attempts_obs

ggsave("../reports/results_rq2_effectiveness/glmm_attempts_trajectory_observed.png",
       p_attempts_obs, width = 6, height = 4, dpi = 150)

# Full-grid dose-response trajectory: all delay × week combinations including
# those that never occurred in the study. Extrapolation beyond the design.
p_attempts_full <- ggplot(plot_data_attempts,
                          aes(study_week, response,
                              colour = `Delay (s)`, fill = `Delay (s)`,
                              group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_x_continuous(breaks = 1:6) +
  labs(x = "Study week", y = "Predicted weekly attempts",
       colour = "Delay (s)", fill = "Delay (s)",
       caption = "All delay × week combinations shown, including counterfactual cells") +
  theme_linedraw()

p_attempts_full

ggsave("../reports/results_rq2_effectiveness/glmm_attempts_trajectory_full.png",
       p_attempts_full, width = 6, height = 4, dpi = 150)

# EMMs at Week 6 only — same format as preregistered EMM plot.
em_attempts_w6 <- plot_data_attempts_cond |>
  filter(round(study_week) == 6) |>
  mutate(condition = factor(condition, levels = condition_order)) |>
  arrange(condition)

p_attempts_w6 <- ggplot(em_attempts_w6,
                        aes(x = condition, y = response,
                            ymin = ci_lower, ymax = ci_upper)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0.2) +
  labs(x = "Condition", y = "Predicted weekly attempts (Week 6)",
       title = "RQ2.2 (exploratory): EMMs at Week 6 — attempt count by condition") +
  theme_linedraw()

p_attempts_w6

ggsave("../reports/results_rq2_effectiveness/glmm_attempts_emm_w6.png",
       p_attempts_w6, width = 5, height = 4, dpi = 150)

```


## Combined comparison on a common (marginal) scale: Preregistered (PP, efficacy) vs Exploratory (ITT, effectiveness) at Week 6

The preregistered `glm.nb` predictions are population-averaged (marginal —
no random effect). The exploratory GLMM `emmeans` would by default return a
*conditional* mean at random-effect = 0 (a "typical" participant), which under
Jensen's inequality is smaller than the marginal mean by a factor of
`exp(σ_u²/2)` (log link) or an analogous adjustment (logit link). To put both
estimators on the same scale, we recompute the GLMM Week 6 emmeans with
`bias.adjust = TRUE` so they return marginal/population-averaged predictions.
Any remaining gap is the genuine selection effect (completers being heavy users).

```{r}

# Mean attempted_w6 in completers — used to normalise the PP dismissal rate
# (which is on the count scale) to a probability, matching the GLMM scale.
mean_att <- mean(df_rq2$attempted_w6, na.rm = TRUE)

# --- Random-intercept SDs (link scale) ---
sigma_dismiss <- sqrt(VarCorr(m_dismiss_cond)$cond$participant_id[1, 1])
sigma_attempts <- sqrt(VarCorr(m_attempts_cond)$cond$participant_id[1, 1])

cat(sprintf("sigma_u (dismiss, logit link): %.3f\n", sigma_dismiss))
cat(sprintf("sigma_u (attempts, log link):  %.3f\n", sigma_attempts))
cat(sprintf("Jensen multiplier for attempts (exp(sigma^2/2)): %.2fx\n",
            exp(sigma_attempts^2 / 2)))

# --- RQ2.1 dismissals: marginal Week 6 emmeans ---
em_dismiss_w6_marg <- emmeans(
  m_dismiss_cond, ~ condition * study_week,
  at          = list(study_week = 6),
  type        = "response",
  bias.adjust = TRUE,
  sigma       = sigma_dismiss
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  rename_with(~ "ci_lower", any_of(c("asymp.LCL", "lower.CL"))) |>
  rename_with(~ "ci_upper", any_of(c("asymp.UCL", "upper.CL"))) |>
  mutate(condition = factor(condition, levels = condition_order)) |>
  arrange(condition)

# --- RQ2.2 attempts: marginal Week 6 emmeans ---
em_attempts_w6_marg <- emmeans(
  m_attempts_cond, ~ condition * study_week_c,
  at          = list(study_week_c = 6 - week_mean),
  type        = "response",
  bias.adjust = TRUE,
  sigma       = sigma_attempts
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  rename_with(~ "ci_lower", any_of(c("asymp.LCL", "lower.CL"))) |>
  rename_with(~ "ci_upper", any_of(c("asymp.UCL", "upper.CL"))) |>
  mutate(
    study_week = study_week_c + week_mean,
    condition  = factor(condition, levels = condition_order)
  ) |>
  arrange(condition)

# --- RQ2.1 combined plot (marginal scale) ---
dismiss_combined_marg <- bind_rows(
  em_pred_rq2_1 |>
    mutate(
      condition = factor(condition, levels = condition_order),
      estimate  = response / mean_att,
      lower     = asymp.LCL / mean_att,
      upper     = asymp.UCL / mean_att,
      Analysis  = "Preregistered (PP, efficacy)"
    ),
  em_dismiss_w6_marg |>
    mutate(
      estimate = prob,
      lower    = ci_lower,
      upper    = ci_upper,
      Analysis = "Exploratory (ITT, effectiveness)"
    )
) |>
  mutate(Analysis = factor(Analysis,
                           levels = c("Preregistered (PP, efficacy)",
                                      "Exploratory (ITT, effectiveness)")))

p_dismiss_combined_marg <- ggplot(dismiss_combined_marg,
  aes(x = condition, y = estimate, ymin = lower, ymax = upper,
      colour = Analysis, shape = Analysis, group = Analysis)) +
  geom_point(size = 3, position = position_dodge(0.4)) +
  geom_errorbar(width = 0.2, position = position_dodge(0.4)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_colour_manual(values = c("Preregistered (PP, efficacy)"     = "#2166ac",
                                 "Exploratory (ITT, effectiveness)" = "#d6604d")) +
  scale_shape_manual(values  = c("Preregistered (PP, efficacy)"     = 16,
                                 "Exploratory (ITT, effectiveness)" = 17)) +
  labs(x = "Condition", y = "Predicted dismissal probability (Week 6)",
       title = "RQ2.1: Dismissal rate at Week 6 — marginal (population-averaged) estimates",
       colour = "Analysis", shape = "Analysis") +
  theme_linedraw() +
  theme(legend.position = "bottom")

p_dismiss_combined_marg

ggsave("../reports/results_rq2_effectiveness/combined_emm_dismiss_w6_marginal.png",
       p_dismiss_combined_marg, width = 6, height = 5, dpi = 150)

# --- RQ2.2 combined plot (marginal scale) ---
attempts_combined_marg <- bind_rows(
  em_pred_rq2_2 |>
    mutate(
      condition = factor(condition, levels = condition_order),
      estimate  = response,
      lower     = asymp.LCL,
      upper     = asymp.UCL,
      Analysis  = "Preregistered (PP, efficacy)"
    ),
  em_attempts_w6_marg |>
    mutate(
      estimate = response,
      lower    = ci_lower,
      upper    = ci_upper,
      Analysis = "Exploratory (ITT, effectiveness)"
    )
) |>
  mutate(Analysis = factor(Analysis,
                           levels = c("Preregistered (PP, efficacy)",
                                      "Exploratory (ITT, effectiveness)")))

p_attempts_combined_marg <- ggplot(attempts_combined_marg,
  aes(x = condition, y = estimate, ymin = lower, ymax = upper,
      colour = Analysis, shape = Analysis, group = Analysis)) +
  geom_point(size = 3, position = position_dodge(0.4)) +
  geom_errorbar(width = 0.2, position = position_dodge(0.4)) +
  scale_colour_manual(values = c("Preregistered (PP, efficacy)"     = "#2166ac",
                                 "Exploratory (ITT, effectiveness)" = "#d6604d")) +
  scale_shape_manual(values  = c("Preregistered (PP, efficacy)"     = 16,
                                 "Exploratory (ITT, effectiveness)" = 17)) +
  labs(x = "Condition", y = "Predicted weekly attempts (Week 6)",
       title = "RQ2.2: Attempt count at Week 6 — marginal (population-averaged) estimates",
       colour = "Analysis", shape = "Analysis") +
  theme_linedraw() +
  theme(legend.position = "bottom")

p_attempts_combined_marg

ggsave("../reports/results_rq2_effectiveness/combined_emm_attempts_w6_marginal.png",
       p_attempts_combined_marg, width = 6, height = 5, dpi = 150)

```

### Proportion change in weekly attempts (Week 1 → Week 6): PP vs ITT

Per-condition proportion change in weekly attempts between Week 1 and Week 6,
estimated from both analyses. The PP estimate uses a NB GLMM fit to the same
completer subsample (`df_rq2`) reshaped to long format, with the analogous
`condition * week + (1 | participant_id)` structure as the ITT model — so the
two estimates are computed in a directly parallel way. The within-model ratio
of predicted means cancels the random-effect Jensen factor, so no bias
adjustment is needed here.

```{r}

# --- PP: long-format GLMM on completers (parallel structure to m_attempts_cond) ---
df_rq2_long <- df_rq2 |>
  dplyr::select(participant_id, condition, attempted_w1, attempted_w6) |>
  pivot_longer(cols      = c(attempted_w1, attempted_w6),
               names_to  = "week",
               values_to = "attempted") |>
  mutate(week = factor(as.integer(str_extract(week, "[0-9]+")),
                       levels = c(1, 6)))

m_attempts_pp <- glmmTMB(
  attempted ~ condition * week + (1 | participant_id),
  data   = df_rq2_long,
  family = nbinom2
)
summary(m_attempts_pp)

# Within-condition W6/W1 rate ratio → proportion change. revpairwise gives
# (level2 - level1) on the link scale = log(rate ratio); type = "response"
# back-transforms to the rate ratio.
get_prop_change <- function(model, week_var, week_at, analysis_label) {
  em <- emmeans(model, as.formula(paste0("~ ", week_var, " | condition")),
                at = setNames(list(week_at), week_var))
  contrast(em, method = "revpairwise") |>
    summary(infer = TRUE, type = "response") |>
    as_tibble() |>
    mutate(
      condition   = factor(condition, levels = condition_order),
      prop_change = ratio - 1,
      prop_lower  = asymp.LCL - 1,
      prop_upper  = asymp.UCL - 1,
      Analysis    = analysis_label
    ) |>
    arrange(condition)
}

prop_change_pp <- get_prop_change(
  m_attempts_pp, "week", factor(c(1, 6), levels = c(1, 6)),
  "Preregistered (PP, efficacy)"
)

prop_change_itt <- get_prop_change(
  m_attempts_cond, "study_week_c", c(1, 6) - week_mean,
  "Exploratory (ITT, effectiveness)"
)

prop_change_combined <- bind_rows(prop_change_pp, prop_change_itt) |>
  mutate(Analysis = factor(Analysis,
                           levels = c("Preregistered (PP, efficacy)",
                                      "Exploratory (ITT, effectiveness)")))

prop_change_table <- prop_change_combined |>
  mutate(
    `Rate ratio (W6/W1)` = signif(ratio, 3),
    `Prop. change`       = scales::percent(prop_change, accuracy = 0.1),
    `95% CI`             = paste0("[",
                                  scales::percent(prop_lower, accuracy = 0.1),
                                  ", ",
                                  scales::percent(prop_upper, accuracy = 0.1),
                                  "]")
  ) |>
  dplyr::select(Analysis, Condition = condition, `Rate ratio (W6/W1)`,
                `Prop. change`, `95% CI`)

prop_change_table |> kable() |> kable_classic()

write_csv(prop_change_table,
          "../reports/results_rq2_effectiveness/combined_prop_change.csv")

p_prop_change_combined <- ggplot(prop_change_combined,
  aes(x = condition, y = prop_change,
      ymin = prop_lower, ymax = prop_upper,
      colour = Analysis, shape = Analysis, group = Analysis)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(size = 3, position = position_dodge(0.4)) +
  geom_errorbar(width = 0.2, position = position_dodge(0.4)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_colour_manual(values = c("Preregistered (PP, efficacy)"     = "#2166ac",
                                 "Exploratory (ITT, effectiveness)" = "#d6604d")) +
  scale_shape_manual(values  = c("Preregistered (PP, efficacy)"     = 16,
                                 "Exploratory (ITT, effectiveness)" = 17)) +
  labs(x = "Condition",
       y = "Proportion change in weekly attempts (Week 1 → Week 6)",
       title = "RQ2.2: Within-condition change in attempts — preregistered vs. exploratory",
       colour = "Analysis", shape = "Analysis") +
  theme_linedraw() +
  theme(legend.position = "bottom")

p_prop_change_combined

ggsave("../reports/results_rq2_effectiveness/combined_prop_change.png",
       p_prop_change_combined, width = 6, height = 5, dpi = 150)

```

# Session info

```{r}
sessionInfo()
```
