---
title: "RQ2: Effectiveness"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(MASS)
library(broom)
library(emmeans)
library(flextable)
library(officer)
library(AER)

dir.create("results_rq2", showWarnings = FALSE)

```

# Load data

```{r}

df_rq2_1 <- readRDS("data_clean/df_rq2_1_model.rds") %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

df_rq2_2 <- readRDS("data_clean/df_rq2_2_model.rds") %>%
  mutate(condition = relevel(factor(condition), ref = "CCC"))

df_rq2_event <- readRDS("data_clean/df_rq2.rds")

```

# RQ 2.1: Dismissed app openings in week 6

Model: NB regression, offset = log(attempted_w6). Covariates: dismissed_w1, attempted_w1.

## Assumption check: overdispersion

```{r}

poisson_21 <- glm(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1,
  offset = log(attempted_w6),
  data   = df_rq2_1,
  family = poisson()
)
disp_test_21 <- dispersiontest(poisson_21)
cat("RQ2.1 dispersion test:", capture.output(print(disp_test_21)), sep = "\n")

zero_pct_21 <- mean(df_rq2_1$dismissed_w6 == 0) * 100
cat(sprintf("RQ2.1 zero proportion: %.1f%%\n", zero_pct_21))

```

## Main model

```{r}

model_rq2_1 <- glm.nb(
  dismissed_w6 ~ condition + dismissed_w1 + attempted_w1 + offset(log(attempted_w6)),
  data = df_rq2_1
)

summary(model_rq2_1)

results_rq2_1 <- tidy(model_rq2_1, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     p.value < .01  ~ "< .01",
                     p.value < .05  ~ "< .05",
                     TRUE           ~ as.character(round(p.value, 3))),
    B_SE = paste0(round(log(estimate), 3), " (", round(std.error, 3), ")")
  ) %>%
  dplyr::select(term, B_SE, RR, CI, p) %>%
  rename(Predictor = term, `B (SE)` = B_SE, `Rate Ratio` = RR, `95% CI` = CI, `p` = p)

print(results_rq2_1)
write_csv(results_rq2_1, "results_rq2/model_rq2_1_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_1 <- emmeans(model_rq2_1, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  p.value < .01  ~ "< .01",
                  p.value < .05  ~ "< .05",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

print(pairwise_rq2_1)
write_csv(pairwise_rq2_1, "results_rq2/pairwise_rq2_1.csv")

```

## Relative reduction: % dismissed of attempted per condition × week

```{r}

df_reduction <- df_rq2_event %>%
  group_by(condition, study_week) %>%
  summarise(
    n_attempted   = sum(initial_attempt),
    n_dismissed   = sum(dismissed),
    pct_dismissed = round(n_dismissed / n_attempted * 100, 1),
    .groups = "drop"
  )

write_csv(df_reduction, "results_rq2/dismissal_rate_by_condition_week.csv")
cat("RQ2.1 dismissal rates:\n"); print(df_reduction)

```

# RQ 2.2: Initial app opening attempts in week 6

Model: NB regression, covariate = initial_w1.

## Assumption check: overdispersion

```{r}

poisson_22 <- glm(
  initial_w6 ~ condition + initial_w1,
  data   = df_rq2_2,
  family = poisson()
)
disp_test_22 <- dispersiontest(poisson_22)
cat("\nRQ2.2 dispersion test:", capture.output(print(disp_test_22)), sep = "\n")

zero_pct_22 <- mean(df_rq2_2$initial_w6 == 0) * 100
cat(sprintf("RQ2.2 zero proportion: %.1f%%\n", zero_pct_22))

```

## Main model

```{r}

model_rq2_2 <- glm.nb(
  initial_w6 ~ condition + initial_w1,
  data = df_rq2_2
)

summary(model_rq2_2)

results_rq2_2 <- tidy(model_rq2_2, exponentiate = TRUE, conf.int = TRUE) %>%
  mutate(
    RR   = round(estimate, 3),
    CI   = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p    = case_when(p.value < .001 ~ "< .001",
                     p.value < .01  ~ "< .01",
                     p.value < .05  ~ "< .05",
                     TRUE           ~ as.character(round(p.value, 3))),
    B_SE = paste0(round(log(estimate), 3), " (", round(std.error, 3), ")")
  ) %>%
  dplyr::select(term, B_SE, RR, CI, p) %>%
  rename(Predictor = term, `B (SE)` = B_SE, `Rate Ratio` = RR, `95% CI` = CI, `p` = p)

print(results_rq2_2)
write_csv(results_rq2_2, "results_rq2/model_rq2_2_results.csv")

```

## Pairwise comparisons

```{r}

pairwise_rq2_2 <- emmeans(model_rq2_2, ~ condition) %>%
  contrast("pairwise", adjust = "none") %>%
  summary(infer = TRUE, type = "response") %>%
  as_tibble() %>%
  mutate(
    across(where(is.numeric), ~ round(.x, 3)),
    p = case_when(p.value < .001 ~ "< .001",
                  p.value < .01  ~ "< .01",
                  p.value < .05  ~ "< .05",
                  TRUE           ~ as.character(round(p.value, 3)))
  )

print(pairwise_rq2_2)
write_csv(pairwise_rq2_2, "results_rq2/pairwise_rq2_2.csv")

```

## Mean initial attempts per user per condition × week

```{r}

df_weekly_attempts <- df_rq2_event %>%
  group_by(participant_id, condition, study_week) %>%
  summarise(initial = sum(initial_attempt), .groups = "drop") %>%
  group_by(condition, study_week) %>%
  summarise(
    n_users      = n(),
    mean_initial = round(mean(initial), 2),
    .groups = "drop"
  )

write_csv(df_weekly_attempts, "results_rq2/weekly_attempts_by_condition.csv")

# Reduction from week 1 to week 6
df_reduction_w1w6 <- df_weekly_attempts %>%
  filter(study_week %in% c(1, 6)) %>%
  pivot_wider(names_from = study_week, values_from = c(mean_initial, n_users),
              names_glue = "{.value}_w{study_week}") %>%
  mutate(
    absolute_reduction = round(mean_initial_w1 - mean_initial_w6, 2),
    relative_reduction = round((mean_initial_w1 - mean_initial_w6) / mean_initial_w1 * 100, 1)
  )

print(df_reduction_w1w6)
write_csv(df_reduction_w1w6, "results_rq2/reduction_w1_to_w6.csv")

```

# Word tables

```{r}

doc <- read_docx() %>%
  body_add_par("RQ2.1: NB Regression — Dismissed Openings (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_1) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_1 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("RQ2.2: NB Regression — Initial App Opening Attempts (Week 6)", style = "heading 1") %>%
  body_add_flextable(flextable(results_rq2_2) %>% autofit()) %>%
  body_add_par("", style = "Normal") %>%
  body_add_par("Pairwise Comparisons", style = "heading 2") %>%
  body_add_flextable(flextable(pairwise_rq2_2 %>%
                                 dplyr::select(contrast, ratio, SE, asymp.LCL, asymp.UCL, p)) %>%
                       autofit())

print(doc, target = "results_rq2/results_rq2.docx")
cat("RQ2 complete. Results saved to results_rq2/\n")

```

# Session info

```{r}
sessionInfo()
```
