---
title: "RQ4: Dropout reasons"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(flextable)
library(officer)

dir.create("results_rq4", showWarnings = FALSE)

```

# Load data

```{r}

df_termination <- readRDS("data_clean/df_termination.rds")
df_rq1         <- readRDS("data_clean/df_rq1.rds")

```

# RQ4: Reasons for terminating study participation

The behavioral CSVs record a `terminationReason` column for participants who explicitly terminated via the app. The only value present is `"terminatedByUser"` (N = 66) — this is a flag rather than a free-text reason category. The preregistered dropout-reason question ("I lost motivation…", "I find one sec unhelpful…", etc.) was a separate in-app screen. If that data was captured in a separate export, it is not in the current behavioral CSVs.

```{r}

cat("Participants with a recorded termination flag:", nrow(df_termination), "\n")
cat("Breakdown by condition:\n")
print(count(df_termination, condition))

# How many of the flagged terminators are in df_rq1 (i.e. had behavioral data)?
termination_with_dropout <- df_termination %>%
  left_join(df_rq1 %>% select(participant_id, dropout, last_week), by = "participant_id")

cat("\nTerminated participants — dropout status:\n")
print(count(termination_with_dropout, condition, dropout, last_week))

```

# Termination summary

Termination flags as % of total dropouts per condition.

```{r}

df_rq1_counts <- df_rq1 %>%
  group_by(condition) %>%
  summarise(n_total = n(), n_dropout = sum(dropout), .groups = "drop")

df_termination_summary <- termination_with_dropout %>%
  count(condition, name = "n_terminated") %>%
  left_join(df_rq1_counts, by = "condition") %>%
  mutate(
    pct_of_dropouts = round(n_terminated / n_dropout * 100, 1),
    pct_of_total    = round(n_terminated / n_total * 100, 1)
  )

print(df_termination_summary)
write_csv(df_termination_summary, "results_rq4/termination_summary.csv")

```

# Word table

```{r}

doc <- read_docx() %>%
  body_add_par("RQ4: Dropout Reasons", style = "heading 1") %>%
  body_add_par(
    paste("Note: behavioral CSVs record only a binary 'terminatedByUser' flag",
          "(N = 66). The preregistered categorical reasons are in a separate",
          "in-app export if available."),
    style = "Normal"
  ) %>%
  body_add_par("", style = "Normal") %>%
  body_add_flextable(flextable(df_termination_summary) %>% autofit())

print(doc, target = "results_rq4/results_rq4.docx")
cat("RQ4 complete. Results saved to results_rq4/\n")

```

# Session info

```{r}
sessionInfo()
```
