---
title: "Manuscript figures and tables"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Produces publication-ready figures and tables from previously saved analysis outputs.
Outputs saved to `../reports/manuscript/`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width = 8, fig.height = 4)
```

# Dependencies

```{r}

library(tidyverse)
library(patchwork)
library(flextable)
library(officer)
library(emmeans)
library(lme4)
library(glmmTMB)

dir.create("../reports/manuscript/", showWarnings = FALSE, recursive = TRUE)

```

# Shared helpers

```{r}

# Add lo/hi columns by parsing a "[lo, hi]" string column
add_ci_cols <- function(df, col = "95% CI") {
  nums <- str_extract_all(df[[col]], "[-0-9.eE+]+") |> map(as.numeric)
  df |> mutate(lo = map_dbl(nums, 1), hi = map_dbl(nums, 2))
}

# Consistent colour palettes
cond_pal   <- c(ABC = "#4477AA", ACC = "#EE6677", BCC = "#228833", CCC = "#CCBB44")
delay_pal  <- c("3" = "#EE6677", "6" = "#228833", "10" = "#4477AA")
cond_order <- c("ABC", "ACC", "BCC", "CCC")

# Shared theme
theme_ms <- function(...) {
  theme_classic(base_size = 12) +
    theme(
      strip.background = element_blank(),
      plot.title       = element_text(size = 11, face = "bold"),
      ...
    )
}

# Minimal flextable formatter
ms_flextable <- function(df, ...) {
  flextable(df, ...) |>
    font(fontname = "Times New Roman", part = "all") |>
    fontsize(size = 10, part = "all") |>
    bold(part = "header") |>
    hline_top(part = "header", border = fp_border(width = 1.5)) |>
    hline_bottom(part = "header", border = fp_border(width = 1)) |>
    hline_bottom(part = "body",   border = fp_border(width = 1.5)) |>
    autofit()
}

```

---

# Main text tables

## Table 1: Participant flow by condition

```{r table-1}

df_flow <- read_csv("../reports/results_rq1_tolerability/dropout_summary.csv",
                    show_col_types = FALSE) |>
  mutate(
    condition    = factor(condition, levels = cond_order),
    dropout_rate = sprintf("%.1f%%", dropout_rate)
  ) |>
  arrange(condition) |>
  rename(
    Condition       = condition,
    `N enrolled`    = n_total,
    `N dropped out` = n_dropout,
    `N completed`   = n_complete,
    `Dropout rate`  = dropout_rate
  )

ms_flextable(df_flow) |>
  set_caption("Table 1. Participant flow by condition.")

write_csv(df_flow, "../reports/manuscript/table1_participant_flow.csv")

```

## Table 2: RQ1 logistic regression — dropout by condition

```{r table-2}

df_rq1_model <- read_csv("../reports/results_rq1_tolerability/model_rq1_results.csv",
                          show_col_types = FALSE) |>
  filter(Predictor != "(Intercept)") |>
  mutate(
    Predictor = str_remove(Predictor, "^condition"),
    Predictor = paste0(Predictor, " vs. CCC")
  ) |>
  rename(
    Condition = Predictor,
    `Odds ratio` = OR,
    `95% CI`     = `95% CI`,
    `p`          = p
  )

ms_flextable(df_rq1_model) |>
  set_caption("Table 2. RQ1: Logistic regression predicting study dropout by condition (reference = CCC).")

write_csv(df_rq1_model, "../reports/manuscript/table2_rq1_model.csv")

```

## Table 3: RQ2 pairwise comparisons — attempts at Week 6

```{r table-3}

df_pw2 <- read_csv("../reports/results_rq2_effectiveness/pairwise_rq2_2.csv",
                    show_col_types = FALSE) |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  mutate(
    `95% CI` = paste0("[", asymp.LCL, ", ", asymp.UCL, "]")
  ) |>
  select(
    Contrast      = contrast,
    `Rate ratio`  = ratio,
    SE,
    `95% CI`,
    `z`           = z.ratio,
    `p`           = p
  )

ms_flextable(df_pw2) |>
  set_caption(
    paste("Table 3. RQ2.2: Pairwise comparisons of predicted app open attempt counts at Week 6",
          "(negative binomial regression; unadjusted p-values).")
  )

write_csv(df_pw2, "../reports/manuscript/table3_rq2_pairwise_attempts.csv")

```

---

# Main text figures

## Figure 1: Attrition by week

Weekly proportion of participants dropping out (last active week), by condition.

```{r figure-1-attrition-week}

install.packages("wesanderson")
library(wesanderson)

fox_subset <- wes_palette("FantasticFox1")[c(1, 2, 3, 5)]
df_weekly_raw <- read_csv("../reports/results_rq1_tolerability/weekly_dropout_counts.csv",
                           show_col_types = FALSE)

df_n_total <- read_csv("../reports/results_rq1_tolerability/dropout_summary.csv",
                        show_col_types = FALSE) |>
  select(condition, n_total)

df_weekly <- df_weekly_raw |>
  pivot_longer(-last_week,
               names_to    = "condition",
               names_prefix = "n_dropouts_",
               values_to   = "n_dropout") |>
  left_join(df_n_total, by = "condition") |>
  mutate(
    condition   = factor(condition, levels = cond_order),
    pct_dropout = n_dropout / n_total * 100
  )

wes_pal <- wes_palette("FantasticFox1", n = length(cond_order))

p_fig1 <- ggplot(df_weekly,
                 aes(x = last_week, y = pct_dropout,
                     colour = condition, group = condition)) +
  # Transition at start of Week 3: ABC, ACC, BCC change delay
  geom_vline(xintercept = 2.5, linetype = "dashed", colour = "grey50", linewidth = 0.6) +
  # Transition at start of Week 5: ABC only (6s → 10s)
  geom_vline(xintercept = 4.5, linetype = "dotted", colour = "grey50", linewidth = 0.6) +
  annotate("text", x = 2.55, y = 39, label = "ABC/ACC/BCC\ntransition",
           hjust = 0, vjust = 1, size = 2.8, colour = "grey40") +
  annotate("text", x = 4.55, y = 39, label = "ABC\ntransition",
           hjust = 0, vjust = 1, size = 2.8, colour = "grey40") +
  geom_line(linewidth = 1) +
  geom_point(size = 2.5) +
  scale_x_continuous(breaks = 1:5,
                     labels = paste("Week", 1:5)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1, accuracy = 1),
                     limits = c(0, 40),
                     breaks = seq(0, 40, by = 10)) +
  scale_colour_manual(values = fox_subset) +
  labs(
    x      = "Study week",
    y      = "Participants dropping out (%)",
    colour = "Condition"
  ) +
  theme_ms()

p_fig1

ggsave("../reports/manuscript/figure1_attrition_by_week.png",
       p_fig1, width = 6, height = 4, dpi = 300)

```

## Figure 2 (supplemental option): RQ1 tolerability — predicted dropout probability by condition

```{r figure-1}

df_emm_logistic <- read_csv("../reports/results_rq1_tolerability/emmeans_rq1.csv",
                              show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(
    condition = factor(Condition, levels = cond_order),
    analysis  = "Preregistered\n(logistic regression)"
  ) |>
  rename(est = `Pr(dropout)`)

df_emm_hazard <- read_csv("../reports/results_rq1_tolerability/hazard_by_condition_emmeans.csv",
                            show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(
    condition = factor(Condition, levels = cond_order),
    analysis  = "Exploratory\n(dose-response hazard model)"
  ) |>
  rename(est = `Pr(dropout)`)

df_emm_rq1 <- bind_rows(df_emm_logistic, df_emm_hazard) |>
  mutate(analysis = factor(analysis, levels = c(
    "Preregistered\n(logistic regression)",
    "Exploratory\n(dose-response hazard model)"
  )))

p_rq1 <- ggplot(df_emm_rq1, aes(x = condition, y = est,
                                   colour = analysis, shape = analysis)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = lo, ymax = hi),
                width = 0, linewidth = 0.8,
                position = position_dodge(width = 0.4)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0.4, 1),
                     breaks = seq(0.4, 1, by = 0.1)) +
  scale_colour_manual(values = c("#4477AA", "#EE6677")) +
  scale_shape_manual(values = c(16, 17)) +
  labs(
    x      = "Condition",
    y      = "Predicted Pr(dropout by Week 6)",
    colour = "Analysis",
    shape  = "Analysis"
  ) +
  theme_ms(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 2), shape = guide_legend(nrow = 2))

p_rq1

ggsave("../reports/manuscript/figure1_rq1_tolerability.png",
       p_rq1, width = 6, height = 5, dpi = 300)

```

## Figure 2: App opening attempts at Week 6 by condition

Estimated marginal means from preregistered negative binomial model (controlling for Week 1 attempts).

```{r figure-2}

df_emm_att <- read_csv("../reports/results_rq2_effectiveness/emmeans_rq2_2.csv",
                        show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(condition = factor(Condition, levels = cond_order))

p_fig2 <- ggplot(df_emm_att,
                 aes(x = condition, y = `Mean attempts`, ymin = lo, ymax = hi)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0, linewidth = 0.8) +
  labs(
    x = "Condition",
    y = "Predicted weekly attempts (Week 6)"
  ) +
  theme_ms()

p_fig2

ggsave("../reports/manuscript/figure2_rq2_attempts_w6.png",
       p_fig2, width = 5, height = 4, dpi = 300)

```

## Figure 3: RQ2 dismissal rate — preregistered and dose-response

Panel A: Estimated marginal means at Week 6 by condition (preregistered NB model).
Panel B: Predicted dismissal probability by delay length (exploratory binomial GLMM; observed cells only).

```{r figure-3-panel-a}

df_emm_dis <- read_csv("../reports/results_rq2_effectiveness/emmeans_rq2_1.csv",
                        show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(condition = factor(Condition, levels = cond_order))

p3a <- ggplot(df_emm_dis,
              aes(x = condition,
                  y = `Dismissals per attempt`,
                  ymin = lo, ymax = hi)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0, linewidth = 0.8) +
  labs(
    x     = "Condition",
    y     = "Predicted dismissals per attempt (Week 6)",
    title = "(A) Preregistered: Week 6 by condition"
  ) +
  theme_ms()

```

```{r figure-3-panel-b}

m_dismiss <- read_rds("../reports/results_rq2_effectiveness/glmm_dismiss.rds")

# Recreate the centred + filtered dataset the dismiss model was fit on
weekly_dismiss_c <- weekly_raw |>
  filter(attempted > 0) |>
  mutate(
    delay_secs_c = delay_secs - delay_mean,
    study_week_c = study_week - week_mean
  )

plot_data_dis <- emmeans(
  m_dismiss, ~ delay_secs_c * study_week_c,
  at   = list(
    delay_secs_c = c(3, 6, 10) - delay_mean,
    study_week_c = (1:6) - week_mean
  ),
  type = "response",
  data = weekly_dismiss_c
) |>
  summary(infer = TRUE) |>
  as_tibble() |>
  mutate(
    delay_secs  = round(delay_secs_c + delay_mean),
    study_week  = round(study_week_c + week_mean),
    `Delay (s)` = factor(delay_secs)
  )

observed_cells_dis <- weekly_dismiss_c |>
  distinct(delay_secs, study_week)

plot_data_dis_obs <- plot_data_dis |>
  semi_join(observed_cells_dis, by = c("delay_secs", "study_week"))

p3b <- ggplot(plot_data_dis_obs,
              aes(study_week, prob,
                  colour = `Delay (s)`, fill = `Delay (s)`,
                  group  = `Delay (s)`)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = 1:6) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_colour_manual(values = delay_pal) +
  scale_fill_manual(values = delay_pal) +
  labs(
    x      = "Study week",
    y      = "Predicted dismissal probability",
    colour = "Delay (s)",
    fill   = "Delay (s)",
    title  = "(B) Exploratory: Dose-response trajectory"
  ) +
  theme_ms()

```

```{r figure-3-combine}

fig3 <- p3a + p3b + plot_layout(widths = c(1, 1.4))

fig3

ggsave("../reports/manuscript/figure3_rq2_dismissals.png",
       fig3, width = 10, height = 4.5, dpi = 300)

```

---

# Supplemental materials

## Table S1: RQ3 satisfaction descriptives by condition

```{r table-s1}

df_post <- read_csv("../data/processed/data_processed_selfreport_post.csv",
                     show_col_types = FALSE) |>
  mutate(condition = factor(condition, levels = cond_order))

satisfaction_items <- c(
  solved_problems  = "Solved consumption problems",
  achieved_goals   = "Achieved consumption goals",
  helpful_problems = "Helpful for solving problems",
  helpful_goals    = "Helpful for achieving goals",
  satisfied_interv = "Satisfied with intervention",
  satisfied_progr  = "Satisfied with progress"
)

df_sat_raw <- map_dfr(names(satisfaction_items), function(item) {
  df_post |>
    group_by(condition) |>
    summarise(
      item = item,
      n    = sum(!is.na(.data[[item]])),
      mean = round(mean(.data[[item]], na.rm = TRUE), 2),
      sd   = round(sd(.data[[item]],   na.rm = TRUE), 2),
      .groups = "drop"
    )
}) |>
  mutate(Item = satisfaction_items[item])

df_sat <- df_sat_raw |>
  mutate(`M (SD)` = paste0(mean, " (", sd, ")")) |>
  select(Item, Condition = condition, n, `M (SD)`) |>
  pivot_wider(names_from = Condition, values_from = c(n, `M (SD)`),
              names_glue = "{Condition}_{.value}") |>
  select(Item,
         starts_with("ABC"), starts_with("ACC"),
         starts_with("BCC"), starts_with("CCC"))

names(df_sat) <- names(df_sat) |>
  str_replace("_n$", " n") |>
  str_replace("_M \\(SD\\)$", " M (SD)")

ms_flextable(df_sat) |>
  set_caption(
    "Table S1. RQ3: Satisfaction descriptives (means and SDs on 1–7 scales) by condition."
  )

write_csv(df_sat, "../reports/manuscript/tableS1_rq3_satisfaction.csv")

```

## Table S2: RQ5 preferred delay pattern

Among respondents who expressed a preference for increasing delays (`prefer_increasing == "Yes"`).

```{r table-s2}

# NOTE: Pattern option labels (Option 1/2/3) come from the survey instrument.
# Add a Description column here once you confirm what each option means.

df_pref <- df_post |>
  filter(prefer_increasing == "Yes", !is.na(pref_pattern)) |>
  count(pref_pattern) |>
  mutate(pct = round(n / sum(n) * 100, 1)) |>
  arrange(desc(n)) |>
  select(Pattern = pref_pattern, N = n, `%` = pct) |>
  mutate(`%` = paste0(`%`, "%"))

cat("Preferred pattern N (among prefer_increasing == 'Yes'):", sum(df_pref$N), "\n")

ms_flextable(df_pref) |>
  set_caption(
    paste0("Table S2. RQ5: Preferred delay pattern among post-survey completers who preferred ",
           "increasing delays (N = ", sum(df_pref$N), ").")
  )

write_csv(df_pref, "../reports/manuscript/tableS2_rq5_preferred_pattern.csv")

```

## Figure S1: RQ2 within-condition change from Week 1 to Week 6

```{r figure-s1}

df_change <- read_csv(
  "../reports/results_rq2_effectiveness/combined_prop_change.csv",
  show_col_types = FALSE
) |>
  add_ci_cols() |>
  mutate(
    condition   = factor(Condition, levels = cond_order),
    Analysis    = factor(Analysis, levels = unique(Analysis)),
    prop_change = as.numeric(str_remove(`Prop. change`, "%"))
  )

p_s1 <- ggplot(df_change,
               aes(x = condition, y = prop_change,
                   colour = Analysis, shape = Analysis)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = lo, ymax = hi),
                width = 0, linewidth = 0.8,
                position = position_dodge(width = 0.4)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1, accuracy = 1)) +
  scale_colour_manual(values = c("#4477AA", "#EE6677")) +
  scale_shape_manual(values = c(16, 17)) +
  labs(
    x      = "Condition",
    y      = "Change in weekly attempts, Week 1 → Week 6",
    colour = "Analysis",
    shape  = "Analysis"
  ) +
  theme_ms(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 2), shape = guide_legend(nrow = 2))

p_s1

ggsave("../reports/manuscript/figureS1_rq2_prop_change.png",
       p_s1, width = 6, height = 5, dpi = 300)

```

---

# Summary of outputs

```{r summary}

outputs <- list.files("../reports/manuscript/", full.names = FALSE)
cat("Files saved to reports/manuscript/:\n")
cat(paste0("  ", outputs), sep = "\n")

```
