---
title: "Manuscript figures and tables"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Produces publication-ready figures and tables from previously saved analysis outputs.
Outputs saved to `../reports/manuscript/`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width = 8, fig.height = 4)
```

# Dependencies

```{r}

library(tidyverse)
library(patchwork)
library(flextable)
library(officer)
library(emmeans)
library(lme4)
library(glmmTMB)

dir.create("../reports/manuscript/", showWarnings = FALSE, recursive = TRUE)

```

# Shared helpers

```{r}

# Add lo/hi columns by parsing a "[lo, hi]" string column
add_ci_cols <- function(df, col = "95% CI") {
  nums <- str_extract_all(df[[col]], "[-0-9.eE+]+") |> map(as.numeric)
  df |> mutate(lo = map_dbl(nums, 1), hi = map_dbl(nums, 2))
}

# Consistent colour palettes
cond_pal   <- c(ABC = "#4477AA", ACC = "#EE6677", BCC = "#228833", CCC = "#CCBB44")
delay_pal  <- c("3" = "#EE6677", "6" = "#228833", "10" = "#4477AA")
cond_order <- c("ABC", "ACC", "BCC", "CCC")

# Shared theme
theme_ms <- function(...) {
  theme_classic(base_size = 12) +
    theme(
      strip.background = element_blank(),
      plot.title       = element_text(size = 11, face = "bold"),
      ...
    )
}

# Minimal flextable formatter
ms_flextable <- function(df, ...) {
  flextable(df, ...) |>
    font(fontname = "Times New Roman", part = "all") |>
    fontsize(size = 10, part = "all") |>
    bold(part = "header") |>
    hline_top(part = "header", border = fp_border(width = 1.5)) |>
    hline_bottom(part = "header", border = fp_border(width = 1)) |>
    hline_bottom(part = "body",   border = fp_border(width = 1.5)) |>
    autofit()
}

```

---

# Main text tables

## Table 1: Participant flow by condition

```{r table-1}

df_flow <- read_csv("../reports/results_rq1_tolerability/dropout_summary.csv",
                    show_col_types = FALSE) |>
  mutate(
    condition    = factor(condition, levels = cond_order),
    dropout_rate = sprintf("%.1f%%", dropout_rate)
  ) |>
  arrange(condition) |>
  rename(
    Condition       = condition,
    `N enrolled`    = n_total,
    `N dropped out` = n_dropout,
    `N completed`   = n_complete,
    `Dropout rate`  = dropout_rate
  )

ms_flextable(df_flow) |>
  set_caption("Table 1. Participant flow by condition.")

write_csv(df_flow, "../reports/manuscript/table1_participant_flow.csv")

```

## Table 2: RQ1 logistic regression — dropout by condition

```{r table-2}

df_rq1_model <- read_csv("../reports/results_rq1_tolerability/model_rq1_results.csv",
                          show_col_types = FALSE) |>
  filter(Predictor != "(Intercept)") |>
  mutate(
    Predictor = str_remove(Predictor, "^condition"),
    Predictor = paste0(Predictor, " vs. CCC")
  ) |>
  rename(
    Condition = Predictor,
    `Odds ratio` = OR,
    `95% CI`     = `95% CI`,
    `p`          = p
  )

ms_flextable(df_rq1_model) |>
  set_caption("Table 2. RQ1: Logistic regression predicting study dropout by condition (reference = CCC).")

write_csv(df_rq1_model, "../reports/manuscript/table2_rq1_model.csv")

```

## Table 3: RQ2 negative binomial regression — dismissed openings and attempts at Week 6

```{r table-3}

df_rq2_1_model <- read_csv("../reports/results_rq2_effectiveness/model_rq2_1_results.csv",
                            show_col_types = FALSE) |>
  mutate(Outcome = "Dismissed openings (Week 6)")

df_rq2_2_model <- read_csv("../reports/results_rq2_effectiveness/model_rq2_2_results.csv",
                            show_col_types = FALSE) |>
  mutate(Outcome = "Initial attempts (Week 6)")

df_rq2_model <- bind_rows(df_rq2_1_model, df_rq2_2_model) |>
  mutate(
    Predictor = str_remove(Predictor, "^condition"),
    Predictor = if_else(str_detect(Predictor, "^(ABC|ACC|BCC)$"),
                         paste0(Predictor, " vs. CCC"), Predictor)
  ) |>
  select(Outcome, Predictor, `Rate Ratio`, `95% CI`, p)

ms_flextable(df_rq2_model) |>
  set_caption(
    paste("Table 3. RQ2: Negative binomial regression models predicting dismissed openings and",
          "initial app-opening attempts at Week 6, controlling for Week 1 behaviour",
          "(reference condition = CCC).")
  )

write_csv(df_rq2_model, "../reports/manuscript/table3_rq2_model.csv")

```

---

# Main text figures

## Figure 1: Participant flow diagram

```{r figure-1-flow}

# NOTE: the pre-survey "started" count (4,483 in the manuscript draft) is not
# computed anywhere in 01_processing_behavioral_data.Rmd or
# 02_processing_surveys.Rmd. Confirm its source (raw Qualtrics export row
# count) and set it explicitly here before using this figure -- do not
# hardcode a number that hasn't been traced back to a script.
n_presurvey_started   <- NA_integer_   # TODO: confirm and fill in
n_presurvey_completed <- 2158
n_behavioral          <- 1641
n_excluded_no_activity <- n_presurvey_completed - n_behavioral
n_completers_w1w6     <- 539

flow_boxes <- tribble(
  ~step, ~label,                                                ~n,   ~x, ~y,
  1,     "Pre-survey started",                                  n_presurvey_started,   0, 5,
  2,     "Completed pre-survey & randomised",                   n_presurvey_completed, 0, 4,
  3,     "Excluded: no behavioural activity",                   n_excluded_no_activity, 1.6, 3.5,
  4,     "Behavioural sample (RQ1 attrition analyses)",         n_behavioral,           0, 3,
  5,     "Completers: active Week 1 and Week 6 (RQ2 efficacy)", n_completers_w1w6,      0, 2
) |>
  mutate(text = paste0(label, "\n(N = ", ifelse(is.na(n), "?", n), ")"))

p_flow <- ggplot(flow_boxes) +
  geom_segment(data = filter(flow_boxes, step %in% c(1,2,4,5)),
               aes(x = x, xend = x, y = y, yend = lead(y)),
               linewidth = 0.5, colour = "grey40",
               arrow = arrow(length = unit(0.15, "cm")), na.rm = TRUE) +
  geom_label(aes(x = x, y = y, label = text), size = 3.2, label.size = 0.4,
             hjust = 0.5) +
  coord_cartesian(xlim = c(-1, 3), ylim = c(1.5, 5.5)) +
  theme_void()

p_flow

ggsave("../reports/manuscript/figure1_participant_flow.png",
       p_flow, width = 6, height = 6, dpi = 300)

```

## Figure 2: Attrition by week

Weekly proportion of at-risk participants dropping out (first week with no
recorded activity), by condition. Percentages are relative to participants still
active the previous week; Week 1 is empty by construction, because retention
requires later activity. Error bars are Wilson 95% CIs.

```{r figure-1-attrition-week}

if (!requireNamespace("wesanderson", quietly = TRUE)) {
  install.packages("wesanderson", repos = "https://cloud.r-project.org")
}
library(wesanderson)

fox_subset <- wes_palette("FantasticFox1")[c(1, 2, 3, 5)]
df_weekly_raw <- read_csv("../reports/results_rq1_tolerability/weekly_dropout_counts.csv",
                           show_col_types = FALSE)

df_n_total <- read_csv("../reports/results_rq1_tolerability/dropout_summary.csv",
                        show_col_types = FALSE) |>
  select(condition, n_total)

df_weekly <- df_weekly_raw |>
  pivot_longer(-last_week,
               names_to    = "condition",
               names_prefix = "n_dropouts_",
               values_to   = "n_dropout") |>
  left_join(df_n_total, by = "condition") |>
  arrange(condition, last_week) |>
  group_by(condition) |>
  mutate(
    # at-risk at the start of this dropout week = total N minus everyone who
    # already dropped out in earlier weeks
    n_at_risk    = n_total - lag(cumsum(n_dropout), default = 0),
    pct_dropout  = n_dropout / n_at_risk * 100,
    # dropout is recorded in the first week with no activity (last active + 1);
    # nobody can drop out in Week 1, so the series runs Weeks 2-6
    dropout_week = last_week + 1L,
    condition    = factor(condition, levels = cond_order)
  ) |>
  ungroup() |>
  # Wilson 95% CI for each weekly dropout proportion
  mutate(
    .z    = qnorm(0.975),
    .phat = n_dropout / n_at_risk,
    .ctr  = (.phat + .z^2 / (2 * n_at_risk)) / (1 + .z^2 / n_at_risk),
    .hw   = .z * sqrt(.phat * (1 - .phat) / n_at_risk +
                      .z^2 / (4 * n_at_risk^2)) / (1 + .z^2 / n_at_risk),
    ci_lo = pmax(0,   (.ctr - .hw) * 100),
    ci_hi = pmin(100, (.ctr + .hw) * 100)
  )

wes_pal <- wes_palette("FantasticFox1", n = length(cond_order))
dodge   <- position_dodge(width = 0.3)

p_fig1 <- ggplot(df_weekly,
                 aes(x = dropout_week, y = pct_dropout,
                     colour = condition, group = condition)) +
  # Delay change at start of Week 3: ABC, ACC, BCC
  geom_vline(xintercept = 2.5, linetype = "dashed", colour = "grey50", linewidth = 0.6) +
  # Delay change at start of Week 5: ABC only (6s → 10s)
  geom_vline(xintercept = 4.5, linetype = "dotted", colour = "grey50", linewidth = 0.6) +
  annotate("text", x = 2.55, y = 42, label = "ABC/ACC/BCC\ntransition",
           hjust = 0, vjust = 1, size = 2.8, colour = "grey40") +
  annotate("text", x = 4.55, y = 42, label = "ABC\ntransition",
           hjust = 0, vjust = 1, size = 2.8, colour = "grey40") +
  geom_line(linewidth = 1) +
  geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi), width = 0.2,
                linewidth = 0.5, alpha = 0.7, position = dodge) +
  geom_point(size = 2.5, position = dodge) +
  scale_x_continuous(breaks = 1:6, labels = paste("Week", 1:6),
                     limits = c(0.5, 6.5)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1, accuracy = 1),
                     limits = c(0, 45),
                     breaks = seq(0, 40, by = 10)) +
  scale_colour_manual(values = fox_subset) +
  labs(
    x      = "Study week",
    y      = "At-risk participants dropping out (%)",
    colour = "Condition"
  ) +
  theme_ms()

p_fig1

ggsave("../reports/manuscript/figure2_attrition_by_week.png",
       p_fig1, width = 6, height = 4, dpi = 300)

```

## Load weekly data for dose-response figures

Source data and centring constants for the exploratory GLMMs (matches the
parameterisation in `04_analysis_rq2_effectiveness.Rmd`). Loaded once here so
both dose-response panels below are self-contained and reproducible without
depending on objects left over from another script's session.

```{r load-weekly-dose-response}

weekly_raw <- read_csv("../data/processed/data_processed_behavioral_data_weekly.csv",
                       show_col_types = FALSE)

delay_mean <- mean(weekly_raw$delay_secs)
week_mean  <- mean(weekly_raw$study_week)

m_attempts <- read_rds("../reports/results_rq2_effectiveness/glmm_attempts.rds")
m_dismiss  <- read_rds("../reports/results_rq2_effectiveness/glmm_dismiss.rds")

# Population-averaged predictions for Figure 4 via g-computation (average
# adjusted predictions): for each delay x week cell we evaluate the fitted
# response for every participant using their own estimated random intercept and
# average over participants. Unlike integrating over an assumed Normal random-
# effect distribution, this does not rely on RE normality (which is violated
# here: the RE distribution is right-skewed, so a Normal integral would badly
# overshoot the observed scale) and reproduces the observed data scale.
# 95% CIs propagate fixed-effect uncertainty by parametric simulation from the
# coefficient covariance matrix (random effects held at their fitted values,
# matching a re.form = NULL average-prediction).
set.seed(20260721)
gcomp_predict <- function(beta, Vb, re, invlink, delays, weeks, nsim = 2000){
  cn   <- names(beta)
  xvec <- function(d, w){
    dc <- d - delay_mean; wc <- w - week_mean
    v <- c("(Intercept)" = 1, "delay_secs_c" = dc, "study_week_c" = wc,
           "delay_secs_c:study_week_c" = dc * wc)
    v[cn]
  }
  B   <- MASS::mvrnorm(nsim, mu = beta, Sigma = Vb)
  out <- tidyr::expand_grid(delay = delays, week = weeks)
  out$est <- NA_real_; out$lo <- NA_real_; out$hi <- NA_real_
  for (i in seq_len(nrow(out))){
    xv <- xvec(out$delay[i], out$week[i])
    out$est[i] <- mean(invlink(sum(beta * xv) + re))
    sim <- vapply(as.numeric(B %*% xv),
                  function(e) mean(invlink(e + re)), numeric(1))
    out$lo[i] <- stats::quantile(sim, 0.025)
    out$hi[i] <- stats::quantile(sim, 0.975)
  }
  out
}

```

## Figure 3: RQ2 estimated means at Week 6 (preregistered)

Both panels show model-estimated marginal means (± 95% CI) from the preregistered
negative binomial models, adjusted for Week 1 behaviour. Panel A shows the
dismissal rate (dismissed openings per attempt) and Panel B shows total app-opening
attempts — presented together because they reflect two complementary aspects of
the same RQ2 outcome measure at Week 6.

```{r figure-3}

df_emm_dis <- read_csv("../reports/results_rq2_effectiveness/emmeans_rq2_1.csv",
                        show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(condition = factor(Condition, levels = cond_order))

p3a <- ggplot(df_emm_dis,
              aes(x = condition,
                  y = `Dismissal rate (%)`,
                  ymin = lo, ymax = hi,
                  colour = condition)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0, linewidth = 0.8) +
  scale_colour_manual(values = fox_subset) +
  labs(
    x     = "Condition",
    y     = "Estimated dismissal rate at Week 6, %\n(adjusted for Week 1 behaviour)",
    title = "(A) Dismissed openings"
  ) +
  theme_ms()

df_emm_att <- read_csv("../reports/results_rq2_effectiveness/emmeans_rq2_2.csv",
                        show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(condition = factor(Condition, levels = cond_order))

p3b <- ggplot(df_emm_att,
              aes(x = condition, y = `Mean attempts`, ymin = lo, ymax = hi,
                  colour = condition)) +
  geom_point(size = 3) +
  geom_errorbar(width = 0, linewidth = 0.8) +
  scale_colour_manual(values = fox_subset) +
  labs(
    x     = "Condition",
    y     = "Estimated attempts at Week 6\n(adjusted for Week 1 behaviour)",
    title = "(B) Initial attempts"
  ) +
  theme_ms() 

fig3 <- p3a + p3b

fig3

ggsave("../reports/manuscript/figure3_rq2_week6_emmeans.png",
       fig3, width = 9, height = 4.5, dpi = 300)

```

## Figure 4: Exploratory dose-response trajectories

Panels A and B show population-averaged predictions (average adjusted
predictions / g-computation over the participant random-effect distribution),
so the level is on the observed data scale rather than the subject-specific
(random effect = 0) scale. Panel A: predicted attempt count by delay length and
study week (exploratory negative binomial GLMM; observed cells only). Panel B:
predicted dismissal probability by delay length and study week (exploratory
binomial GLMM; observed cells only). Panel C: number of participants still active each week,
grouped by condition and coloured by the delay each condition was under that
week. Shaded bands mark the weeks where all three delays were observed
(Weeks 1-2) versus where all conditions had converged on 10 s, leaving no delay
variation (Weeks 5-6). Not preregistered.

```{r figure-4-panel-a}

plot_data_att <- gcomp_predict(
  beta    = glmmTMB::fixef(m_attempts)$cond,
  Vb      = as.matrix(vcov(m_attempts)$cond),
  re      = glmmTMB::ranef(m_attempts)$cond$participant_id[[1]],
  invlink = exp,
  delays  = c(3, 6, 10), weeks = 1:6
) |>
  transmute(
    study_week  = week,
    delay_secs  = delay,
    `Delay (s)` = factor(delay_secs),
    response    = est,
    asymp.LCL   = lo,
    asymp.UCL   = hi
  )

observed_cells_att <- weekly_raw |>
  distinct(delay_secs, study_week)

plot_data_att_obs <- plot_data_att |>
  semi_join(observed_cells_att, by = c("delay_secs", "study_week"))

# Shaded bands: Weeks 1-2 (all three delays present) and Weeks 5-6 (all
# conditions at 10 s, no delay variation). Reused across all three panels.
# Only Panel C draws the "Delay (s)" legend; the trajectory layers set
# show.legend = FALSE so patchwork collects a single legend.
dose_bands <- list(
  annotate("rect", xmin = 0.5, xmax = 2.5, ymin = -Inf, ymax = Inf,
           fill = "grey70", alpha = 0.18),
  annotate("rect", xmin = 4.5, xmax = 6.5, ymin = -Inf, ymax = Inf,
           fill = "grey70", alpha = 0.18)
)

p4a <- ggplot(plot_data_att_obs,
              aes(study_week, response,
                  colour = `Delay (s)`, fill = `Delay (s)`,
                  group  = `Delay (s)`)) +
  dose_bands +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA, show.legend = FALSE) +
  geom_line(linewidth = 1, show.legend = FALSE) +
  geom_point(size = 2, show.legend = FALSE) +
  annotate("text", x = 1.5, y = Inf, label = "All three delays observed",
           vjust = 1.6, size = 2.8, colour = "grey30") +
  annotate("text", x = 5.5, y = Inf, label = "No delay variation",
           vjust = 1.6, size = 2.8, colour = "grey30") +
  scale_x_continuous(breaks = 1:6, limits = c(0.5, 6.5)) +
  scale_colour_manual(values = delay_pal) +
  scale_fill_manual(values = delay_pal) +
  labs(
    x      = NULL,
    y      = "Predicted weekly attempts",
    title  = "(A) Attempts"
  ) +
  theme_ms()

```

```{r figure-4-panel-b}

weekly_dismiss_c <- weekly_raw |>
  filter(attempted > 0) |>
  mutate(
    delay_secs_c = delay_secs - delay_mean,
    study_week_c = study_week - week_mean
  )

plot_data_dis <- gcomp_predict(
  beta    = lme4::fixef(m_dismiss),
  Vb      = as.matrix(vcov(m_dismiss)),
  re      = lme4::ranef(m_dismiss)$participant_id[[1]],
  invlink = plogis,
  delays  = c(3, 6, 10), weeks = 1:6
) |>
  transmute(
    study_week  = week,
    delay_secs  = delay,
    `Delay (s)` = factor(delay_secs),
    prob        = est,
    asymp.LCL   = lo,
    asymp.UCL   = hi
  )

observed_cells_dis <- weekly_dismiss_c |>
  distinct(delay_secs, study_week)

plot_data_dis_obs <- plot_data_dis |>
  semi_join(observed_cells_dis, by = c("delay_secs", "study_week"))

p4b <- ggplot(plot_data_dis_obs,
              aes(study_week, prob,
                  colour = `Delay (s)`, fill = `Delay (s)`,
                  group  = `Delay (s)`)) +
  dose_bands +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              alpha = 0.15, colour = NA, show.legend = FALSE) +
  geom_line(linewidth = 1, show.legend = FALSE) +
  geom_point(size = 2, show.legend = FALSE) +
  scale_x_continuous(breaks = 1:6, limits = c(0.5, 6.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_colour_manual(values = delay_pal) +
  scale_fill_manual(values = delay_pal) +
  labs(
    x      = NULL,
    y      = "Predicted dismissal probability",
    title  = "(B) Dismissed openings"
  ) +
  theme_ms()

```

```{r figure-4-panel-c}

# Active participants per condition per week, with the delay each condition was
# under that week (drives the fill colour, shared with Panels A and B).
n_active_wk <- weekly_raw |>
  group_by(condition, study_week) |>
  summarise(n_active   = n_distinct(participant_id),
            delay_secs = first(delay_secs), .groups = "drop") |>
  mutate(
    `Delay (s)` = factor(delay_secs, levels = c(3, 6, 10)),
    condition   = factor(condition, levels = cond_order)
  )

p4c <- ggplot(n_active_wk,
              aes(study_week, n_active, fill = `Delay (s)`, group = condition)) +
  dose_bands +
  geom_col(position = position_dodge(width = 0.85), width = 0.8,
           colour = "white", linewidth = 0.2) +
  geom_text(aes(y = 8, label = condition),
            position = position_dodge(width = 0.85),
            angle = 90, hjust = 0, size = 2.3, colour = "white") +
  scale_x_continuous(breaks = 1:6, limits = c(0.5, 6.5)) +
  scale_fill_manual(values = delay_pal) +
  labs(
    x     = "Study week",
    y     = "Active participants",
    title = "(C) Active participants by condition"
  ) +
  theme_ms()

```

```{r figure-4-combine, fig.width=8, fig.height=10.5}

fig4 <- p4a / p4b / p4c + plot_layout(guides = "collect")

fig4

ggsave("../reports/manuscript/figure4_dose_response.png",
       fig4, width = 8, height = 10.5, dpi = 300)

```

---

# Supplemental materials

## Figure S1: RQ1 tolerability — predicted dropout probability by condition (preregistered vs. dose-response hazard model)

```{r figure-s1-hazard}

df_emm_logistic <- read_csv("../reports/results_rq1_tolerability/emmeans_rq1.csv",
                              show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(
    condition = factor(Condition, levels = cond_order),
    analysis  = "Preregistered\n(logistic regression)"
  ) |>
  rename(est = `Pr(dropout)`)

df_emm_hazard <- read_csv("../reports/results_rq1_tolerability/hazard_by_condition_emmeans.csv",
                            show_col_types = FALSE) |>
  add_ci_cols() |>
  mutate(
    condition = factor(Condition, levels = cond_order),
    analysis  = "Exploratory\n(dose-response hazard model)"
  ) |>
  rename(est = `Pr(dropout)`)

df_emm_rq1 <- bind_rows(df_emm_logistic, df_emm_hazard) |>
  mutate(analysis = factor(analysis, levels = c(
    "Preregistered\n(logistic regression)",
    "Exploratory\n(dose-response hazard model)"
  )))

p_rq1 <- ggplot(df_emm_rq1, aes(x = condition, y = est,
                                   colour = analysis, shape = analysis)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = lo, ymax = hi),
                width = 0, linewidth = 0.8,
                position = position_dodge(width = 0.4)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0.4, 1),
                     breaks = seq(0.4, 1, by = 0.1)) +
  scale_colour_manual(values = c("#4477AA", "#EE6677")) +
  scale_shape_manual(values = c(16, 17)) +
  labs(
    x      = "Condition",
    y      = "Predicted Pr(dropout by Week 6)",
    colour = "Analysis",
    shape  = "Analysis"
  ) +
  theme_ms(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 2), shape = guide_legend(nrow = 2))

p_rq1

ggsave("../reports/manuscript/figureS1_rq1_tolerability.png",
       p_rq1, width = 6, height = 5, dpi = 300)

```

## Table S3: RQ2 pairwise comparisons — dismissed openings and attempts at Week 6

```{r table-s3}

df_pw1 <- read_csv("../reports/results_rq2_effectiveness/pairwise_rq2_1.csv",
                    show_col_types = FALSE) |>
  mutate(Outcome = "Dismissed openings (Week 6)")

df_pw2 <- read_csv("../reports/results_rq2_effectiveness/pairwise_rq2_2.csv",
                    show_col_types = FALSE) |>
  mutate(Outcome = "Initial attempts (Week 6)")

df_pw_all <- bind_rows(df_pw1, df_pw2) |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  mutate(`95% CI` = paste0("[", asymp.LCL, ", ", asymp.UCL, "]")) |>
  select(
    Outcome,
    Contrast     = contrast,
    `Rate ratio` = ratio,
    SE,
    `95% CI`,
    `z`          = z.ratio,
    `p`          = p
  )

ms_flextable(df_pw_all) |>
  set_caption(
    paste("Table S3. RQ2: Pairwise comparisons of model-estimated dismissed openings and",
          "initial attempt counts at Week 6 (negative binomial regression; unadjusted p-values).")
  )

write_csv(df_pw_all, "../reports/manuscript/tableS3_rq2_pairwise.csv")

```

## Table S4: Exploratory GLMM fixed effects — attempts and dismissed openings

```{r table-s4}

df_glmm_att <- read_csv("../reports/results_rq2_effectiveness/glmm_attempts_results.csv",
                          show_col_types = FALSE) |>
  mutate(Outcome = "App-opening attempts (NB GLMM)")

df_glmm_dis <- read_csv("../reports/results_rq2_effectiveness/glmm_dismiss_results.csv",
                          show_col_types = FALSE) |>
  mutate(Outcome = "Dismissed openings (binomial GLMM)")

df_glmm_all <- bind_rows(df_glmm_att, df_glmm_dis) |>
  mutate(
    Predictor = recode(Predictor,
      "(Intercept)"              = "Intercept",
      "delay_secs_c"             = "Delay (seconds, centred)",
      "study_week_c"             = "Study week (centred)",
      "delay_secs_c:study_week_c" = "Delay × Week"
    )
  ) |>
  select(Outcome, Predictor, everything())

ms_flextable(df_glmm_all) |>
  set_caption(
    paste("Table S4. Exploratory GLMM fixed effects for app-opening attempts",
          "(negative binomial, IRRs) and dismissed openings (binomial, ORs).",
          "Predictors are mean-centred. Reference: mean delay (7.5s), mean week (2.9).")
  )

write_csv(df_glmm_all, "../reports/manuscript/tableS4_glmm_fixed_effects.csv")

```

## Table S5: Exploratory GLMM per-week delay slopes — attempts and dismissed openings

```{r table-s5}

df_slopes_att <- read_csv("../reports/results_rq2_effectiveness/glmm_attempts_slopes.csv",
                            show_col_types = FALSE) |>
  mutate(Outcome = "App-opening attempts (IRR per second of delay)")

df_slopes_dis <- read_csv("../reports/results_rq2_effectiveness/glmm_dismiss_slopes.csv",
                            show_col_types = FALSE) |>
  mutate(Outcome = "Dismissed openings (OR per second of delay)")

df_slopes_all <- bind_rows(df_slopes_att, df_slopes_dis) |>
  select(Outcome, `Study week`, everything())

ms_flextable(df_slopes_all) |>
  set_caption(
    paste("Table S5. Exploratory GLMM: estimated effect of delay duration",
          "(per additional second) on app-opening attempts and dismissed openings",
          "at Weeks 1, 3, and 6, derived from the delay × week interaction.")
  )

write_csv(df_slopes_all, "../reports/manuscript/tableS5_glmm_slopes.csv")

```

## Table S1: RQ3 satisfaction descriptives by condition

```{r table-s1}

df_post <- read_csv("../data/processed/data_processed_selfreport_post.csv",
                     show_col_types = FALSE) |>
  mutate(condition = factor(condition, levels = cond_order))

satisfaction_items <- c(
  solved_problems  = "Solved consumption problems",
  achieved_goals   = "Achieved consumption goals",
  helpful_problems = "Helpful for solving problems",
  helpful_goals    = "Helpful for achieving goals",
  satisfied_interv = "Satisfied with intervention",
  satisfied_progr  = "Satisfied with progress"
)

df_sat_raw <- map_dfr(names(satisfaction_items), function(item) {
  df_post |>
    group_by(condition) |>
    summarise(
      item = item,
      n    = sum(!is.na(.data[[item]])),
      mean = round(mean(.data[[item]], na.rm = TRUE), 2),
      sd   = round(sd(.data[[item]],   na.rm = TRUE), 2),
      .groups = "drop"
    )
}) |>
  mutate(Item = satisfaction_items[item])

df_sat <- df_sat_raw |>
  mutate(`M (SD)` = paste0(mean, " (", sd, ")")) |>
  select(Item, Condition = condition, n, `M (SD)`) |>
  pivot_wider(names_from = Condition, values_from = c(n, `M (SD)`),
              names_glue = "{Condition}_{.value}") |>
  select(Item,
         starts_with("ABC"), starts_with("ACC"),
         starts_with("BCC"), starts_with("CCC"))

names(df_sat) <- names(df_sat) |>
  str_replace("_n$", " n") |>
  str_replace("_M \\(SD\\)$", " M (SD)")

ms_flextable(df_sat) |>
  set_caption(
    "Table S1. RQ3: Satisfaction descriptives (means and SDs on 1–7 scales) by condition."
  )

write_csv(df_sat, "../reports/manuscript/tableS1_rq3_satisfaction.csv")

```

## Table S2: RQ5 preferred delay pattern

Among respondents who expressed a preference for increasing delays (`prefer_increasing == "Yes"`).

```{r table-s2}

# NOTE: Pattern option labels (Option 1/2/3) come from the survey instrument.
# Add a Description column here once you confirm what each option means.

df_pref <- df_post |>
  filter(prefer_increasing == "Yes", !is.na(pref_pattern)) |>
  count(pref_pattern) |>
  mutate(pct = round(n / sum(n) * 100, 1)) |>
  arrange(desc(n)) |>
  select(Pattern = pref_pattern, N = n, `%` = pct) |>
  mutate(`%` = paste0(`%`, "%"))

cat("Preferred pattern N (among prefer_increasing == 'Yes'):", sum(df_pref$N), "\n")

ms_flextable(df_pref) |>
  set_caption(
    paste0("Table S2. RQ5: Preferred delay pattern among post-survey completers who preferred ",
           "increasing delays (N = ", sum(df_pref$N), ").")
  )

write_csv(df_pref, "../reports/manuscript/tableS2_rq5_preferred_pattern.csv")

```

## Figure S2: RQ2 within-condition change from Week 1 to Week 6

```{r figure-s1}

df_change <- read_csv(
  "../reports/results_rq2_effectiveness/combined_prop_change.csv",
  show_col_types = FALSE
) |>
  add_ci_cols() |>
  mutate(
    condition   = factor(Condition, levels = cond_order),
    Analysis    = factor(Analysis, levels = unique(Analysis)),
    prop_change = as.numeric(str_remove(`Prop. change`, "%"))
  )

p_s1 <- ggplot(df_change,
               aes(x = condition, y = prop_change,
                   colour = Analysis, shape = Analysis)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = lo, ymax = hi),
                width = 0, linewidth = 0.8,
                position = position_dodge(width = 0.4)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1, accuracy = 1)) +
  scale_colour_manual(values = c("#4477AA", "#EE6677")) +
  scale_shape_manual(values = c(16, 17)) +
  labs(
    x      = "Condition",
    y      = "Change in weekly attempts, Week 1 → Week 6",
    colour = "Analysis",
    shape  = "Analysis"
  ) +
  theme_ms(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 2), shape = guide_legend(nrow = 2))

p_s1

ggsave("../reports/manuscript/figureS1_rq2_prop_change.png",
       p_s1, width = 6, height = 5, dpi = 300)

```

---

# Summary of outputs

```{r summary}

outputs <- list.files("../reports/manuscript/", full.names = FALSE)
cat("Files saved to reports/manuscript/:\n")
cat(paste0("  ", outputs), sep = "\n")

```
